---
title: "Prep for Ameriflux - Churchill"
author: "Kyle Arndt"
date: "2024-02-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/GitHub/churchill_cleaning_processing/') #use this to set your directory
```

Libraries
```{r}
rm(list = ls())
library(data.table)
library(ggplot2)
library(dplyr)
library(zoo)
library(stringr)
Sys.setenv(TZ = "UTC")
```

Load Data
```{r}

df = fread(input = "./outputs/gapfilling/cf3_gapfilled_clean_2022_2025.csv")

```

Format the time stamps at start and end
```{r}
TIMESTAMP_END = df$TIMESTAMP

yeare = format(TIMESTAMP_END,"%Y")
monthe = format(TIMESTAMP_END,"%m")
daye = format(TIMESTAMP_END,"%d")
houre = format(TIMESTAMP_END,"%H")
mine = format(TIMESTAMP_END,"%M")

TIMESTAMP_END = paste(yeare,monthe,daye,houre,mine,sep = '')

TIMESTAMP_START = df$TIMESTAMP - 30*60

years = format(TIMESTAMP_START,"%Y")
months = format(TIMESTAMP_START,"%m")
days = format(TIMESTAMP_START,"%d")
hours = format(TIMESTAMP_START,"%H")
mins = format(TIMESTAMP_START,"%M")

TIMESTAMP_START = paste(years,months,days,hours,mins,sep = '')
rm(daye,days,mine,mins,houre,hours,monthe,months,yeare,years)
```

Format and name data according to Ameriflux Standards. Also do unit conversions.
```{r}
#gas concentrations and variance ################################
CO2 = df$co2_mole_fraction
CH4 = ifelse(df$ch4_mole_fraction<0,NA,df$ch4_mole_fraction*1000) #convert from umol to nmol
H2O = df$h2o_mole_fraction

CO2_MIXING_RATIO = df$co2_mixing_ratio
CH4_MIXING_RATIO = ifelse(df$ch4_mixing_ratio<0,NA,df$ch4_mixing_ratio*1000) #convert from umol to nmol
#H2O mole fraction and H2O mixing ratio are identical


#standard deviation of co2 wet fraction. (Standard deviation is sqrt of the variance, need to)
# CO2_SIGMA = sqrt(df$co2_var)
# CH4_SIGMA = sqrt(df$ch4_var*1000)
# H2O_SIGMA = sqrt(df$h2o_var)

#Gas Fluxes ######################
#CO2 flux is umol m-2 s-1
FC   = df$co2_flux.c
FC_F = ifelse(is.na(df$co2_flux.c),df$rfnee,df$co2_flux.c)
FCH4 = df$ch4_flux.c*1000 #convert from umol m-2 s-1 to nmol m-2 s-1
FCH4_F = ifelse(is.na(df$ch4_flux.c),df$rfch4,df$ch4_flux.c)*1000 #convert from umol m-2 s-1 to nmol m-2 s-1
FH2O = ifelse(df$h2o_flux > 10, NA, df$h2o_flux) # removes a few crazy values

GPP_F   = df$GPP_f
GPP_DT  = df$GPP_DT
RECO    = df$Reco
RECO_DT = df$Reco_DT

#energy fluxes ###########################
G_1_1_1 = df$SHF_6_37_1_1_1.c
G_2_1_1 = df$SHF_6_37_2_1_1.c
H       = df$H.c
LE      = df$LE.c

#Pressure Transducer
WTD_1_1_1 = df$WTD_10_42_1_1_1.c # water table depth in m
TW        = df$TW_2_45_1_1_1 # Water temperature in deg C

#meteorology and weather #################################
TA      = df$TA_2_1_1_1_1    # Air T in Deg C
SVP     = 610.7*10^((7.5*TA)/(237.3+TA)) #NOT INCLUDED IN FINAL
PA      = df$PA_4_2_1_1_1.c    # air pressure in kPA
RH      = df$RH_19_3_1_1_1.c   #RH in %
T_SONIC = df$sonic_temperature-273.15 #sonic temp in Deg C
VPD     = ((100 - RH)/100)*SVP/100 #VPD in hPA
D_SNOW  = ifelse(df$SD_10_99_1_1_1.c == 0,NA,df$SD_10_99_1_1_1.c*100)  # snow depth in cm, standardize summer values between years
P       = df$P_RAIN_8_19_1_1_1 # rain in mm


#Radiation #####################################
ALB = df$ALB_1_1_1.c*100 #albedo in %

LW_IN  = df$LWIN_6_14_1_1_1.c  # Wm-2
LW_OUT = df$LWOUT_6_15_1_1_1.c # Wm-2
SW_IN = df$SWIN_6_10_1_1_1.c   # Wm-2
SW_OUT = df$SWOUT_6_11_1_1_1.c # Wm-2

NETRAD = df$RN_6_5_1_1_1.c     # Wm-2

PPFD_IN = df$PPFD_7_21_1_1_1.c   # par in umol m-2 s-1
PPFD_OUT = df$PPFDR_7_23_1_1_1.c # par out umol m-2 s-1

#Soil factors ###################################
#all swc in %
SWC_1_1_1 = df$SWC_12_36_1_1_1
SWC_2_1_1 = df$SWC_12_36_2_1_1
SWC_2_2_1 = df$SWC_12_36_2_2_1

#all soil temps deg C
TS_1_1_1 = df$TS_2_38_1_1_1.c
TS_2_1_1 = df$TS_2_38_2_1_1.c
TS_2_2_1 = df$TS_2_38_2_2_1.c

TS_3_1_1  = df$TS_2_38_3_1_1.c
TS_3_2_1  = df$TS_2_38_3_2_1.c
TS_3_3_1  = df$TS_2_38_3_3_1.c
TS_3_4_1  = df$TS_2_38_3_4_1.c
TS_3_5_1  = df$TS_2_38_3_5_1.c
TS_3_6_1  = df$TS_2_38_3_6_1.c
TS_3_7_1  = df$TS_2_38_3_7_1.c
TS_3_8_1  = df$TS_2_38_3_8_1.c
TS_3_9_1  = df$TS_2_38_3_9_1.c
TS_3_10_1 = df$TS_2_38_3_10_1.c
TS_3_11_1 = df$TS_2_38_3_11_1.c
TS_3_12_1 = ifelse(df$TS_2_38_3_12_1.c < -3, NA, df$TS_2_38_3_12_1.c) # get rid of weird 2022 data

TS_4_1_1  = df$TS_2_38_4_1_1.c
TS_4_2_1  = df$TS_2_38_4_2_1.c
TS_4_3_1  = df$TS_2_38_4_3_1.c
TS_4_4_1  = df$TS_2_38_4_4_1.c
TS_4_5_1  = df$TS_2_38_4_5_1.c
TS_4_6_1  = df$TS_2_38_4_6_1.c
TS_4_7_1  = df$TS_2_38_4_7_1.c
TS_4_8_1  = df$TS_2_38_4_8_1.c
TS_4_9_1  = df$TS_2_38_4_9_1.c
TS_4_10_1 = df$TS_2_38_4_10_1.c
TS_4_11_1 = df$TS_2_38_4_11_1.c
TS_4_12_1 = df$TS_2_38_4_12_1.c

#wind and turbulence parameters ##############################
MO_LENGTH = df$L
ZL        = df$`(z-d)/L`
TAU       = df$Tau.c

U_SIGMA = sqrt(df$u_var)
V_SIGMA = sqrt(df$v_var)
W_SIGMA = sqrt(df$w_var)

USTAR = df$`u*`

WD     = df$WD_20_35_1_1_1
WS     = df$WS_16_33_1_1_1
WS_MAX = df$MWS_16_34_1_1_1

#Quality flags from EP (Mauder and Foken) ################
FC_SSITC_TEST   = df$qc_co2_flux
FCH4_SSITC_TEST = df$qc_ch4_flux
H_SSITC_TEST    = df$qc_H
LE_SSITC_TEST   = df$qc_LE
TAU_SSITC_TEST  = df$qc_Tau
```

Plots
```{r}
plot(CO2) #umol
plot(CH4) #nmol
plot(H2O) #mmol
```

```{r}
plot(CO2_MIXING_RATIO) #umol
plot(CH4_MIXING_RATIO) #nmol
```

```{r}
# plot(CO2_SIGMA)
# plot(CH4_SIGMA) 
# plot(H2O_SIGMA) 
```

```{r}
plot(FC)
# plot(FC_F)
plot(FCH4)
# plot(FCH4_F)
plot(FH2O)
# plot(GPP_F)
# plot(GPP_DT)
# plot(RECO)
# plot(RECO_DT)
```

```{r}
plot(G_1_1_1)
plot(G_2_1_1)
plot(H)
plot(LE)
```

```{r}
plot(PA)     
plot(RH)
plot(T_SONIC)
plot(TA)   
plot(VPD) 
plot(D_SNOW)
plot(P)
plot(WTD_1_1_1)
```

```{r}
plot(ALB)
plot(LW_IN)
plot(LW_OUT)
plot(SW_IN)
plot(SW_OUT)
plot(NETRAD)
plot(PPFD_IN)
plot(PPFD_OUT)
```

```{r}
plot(SWC_1_1_1)
plot(SWC_2_1_1)
plot(SWC_2_2_1)

plot(TS_1_1_1)
plot(TS_2_1_1)
plot(TS_2_2_1)
```

```{r}
plot(TS_3_1_1)
plot(TS_3_2_1)
plot(TS_3_3_1)
plot(TS_3_4_1)
plot(TS_3_5_1)
plot(TS_3_6_1)
plot(TS_3_7_1)
plot(TS_3_8_1)
plot(TS_3_9_1)
plot(TS_3_10_1)
plot(TS_3_11_1)
plot(TS_3_12_1)

plot(TS_4_1_1)
plot(TS_4_2_1)
plot(TS_4_3_1)
plot(TS_4_4_1)
plot(TS_4_5_1)
plot(TS_4_6_1)
plot(TS_4_7_1)
plot(TS_4_8_1)
plot(TS_4_9_1)
plot(TS_4_10_1)
plot(TS_4_11_1)
plot(TS_4_12_1)
```


```{r}
plot(MO_LENGTH)
plot(ZL)
plot(TAU)
plot(U_SIGMA)
plot(V_SIGMA)
plot(W_SIGMA)
plot(USTAR)
plot(WD)
plot(WS)
plot(WS_MAX)
```

```{r}
plot(FC_SSITC_TEST)
plot(FCH4_SSITC_TEST)
plot(H_SSITC_TEST)
plot(LE_SSITC_TEST)
plot(TAU_SSITC_TEST)
```



############# Create Internal File #########################

Variables to include in internal file: Uncleaned co2, ch4, LE, H, Tau, signal strength, DOY, hour, month, U, V, W, uncleaned biomet??, u flag, Footprint model (needs eddypro re-run before this fully works), random error (once calculated), add ERA5 original data variables

```{r}

# Uncleaned fluxes
FC_UC   = df$co2_flux
FCH4_UC = df$ch4_flux*1000 #convert from umol m-2 s-1 to nmol m-2 s-1
TAU_UC = df$Tau
H_UC = df$H
LE_UC = df$LE

#Signal strength
RSSI_77 = df$rssi_77_mean
SIG_STRENGTH_72 = df$co2_signal_strength_7200_mean

#DOY, hour, month
DOY = df$DOY
HOUR = df$hour
MONTH = df$month

#U Flag 
U_FLAG = df$u_flag

#Wind components - replace these with mean
U = df$u_unrot
V = df$v_unrot
W = df$w_unrot

#Footprint model
X_OFFSET = df$x_offset
X_PEAK = df$x_peak
X_10 = df$`x_10%`
X_30 = df$`x_30%`
X_50 = df$`x_50%`
X_70 = df$`x_70%`
X_90 = df$`x_90%`

#ERA5 Data
DEW_ERA5 = df$dew
ST1_ERA5 = df$st1
ST2_ERA5 = df$st2
LE_ERA5 = df$le
PRES_ERA5 = df$pres
H_ERA5 = df$h
RAD_ERA5 = df$rad
AIRT_ERA5 = df$airt
PPT_ERA5 = df$ppt
U_ERA5 = df$u
V_ERA5 = df$v
VWC1_ERA5 = df$vwc1
VWC2_ERA5 = df$vwc2

# Random error

RAND_ERR_CO2_FLUX = df$rand_err_co2_flux
RAND_ERR_CH4_FLUX = df$rand_err_ch4_flux
RAND_ERR_H2O_FLUX = df$rand_err_h2o_flux
RAND_ERR_TAU = df$rand_err_Tau
RAND_ERR_LE = df$rand_err_LE
RAND_ERR_H = df$rand_err_H

```

```{r}

plot(FC_F)
plot(FCH4_F)
plot(GPP_F)
plot(GPP_DT)
plot(RECO)
plot(RECO_DT)


plot(FC_UC)
plot(FCH4_UC)
plot(H_UC)
plot(LE_UC)
plot(TAU_UC)

plot(RSSI_77)
plot(SIG_STRENGTH_72)

plot(DOY)
plot(HOUR)
plot(MONTH)

plot(U_FLAG)

plot(U)
plot(V)
plot(W)

#These will work after new eddypro runs
plot(X_OFFSET)
plot(X_PEAK)
plot(X_10)
plot(X_30)
plot(X_50)
plot(X_70)
plot(X_90)

plot(DEW_ERA5)
plot(ST1_ERA5)
plot(ST2_ERA5)
plot(LE_ERA5)
plot(PRES_ERA5)
plot(H_ERA5)
plot(RAD_ERA5)
plot(AIRT_ERA5)
plot(PPT_ERA5)
plot(U_ERA5)
plot(V_ERA5)
plot(VWC1_ERA5)
plot(VWC2_ERA5)

plot(RAND_ERR_CO2_FLUX)
plot(RAND_ERR_CH4_FLUX)
plot(RAND_ERR_H2O_FLUX)
plot(RAND_ERR_H)
plot(RAND_ERR_LE)
plot(RAND_ERR_TAU)

```

# Create internal dataframe
```{r}
INTERNAL = data.frame(TIMESTAMP_START,TIMESTAMP_END,
  CO2,CH4,H2O
,CO2_MIXING_RATIO,CH4_MIXING_RATIO
#,CO2_SIGMA,CH4_SIGMA ,H2O_SIGMA 
,FC,FCH4,FH2O
,FC_F,FCH4_F,GPP_F,GPP_DT,RECO,RECO_DT
,G_1_1_1,G_2_1_1
,H
,LE
,PA     
,RH
,T_SONIC
,TA   
,VPD 
,D_SNOW
,P
,WTD_1_1_1
,ALB
,LW_IN
,LW_OUT
,SW_IN
,SW_OUT
,NETRAD
,PPFD_IN
,PPFD_OUT
,SWC_1_1_1
,SWC_2_1_1
,SWC_2_2_1
,TS_1_1_1
,TS_2_1_1
,TS_2_2_1
,TS_3_1_1
,TS_3_2_1
,TS_3_3_1
,TS_3_4_1
,TS_3_5_1
,TS_3_6_1
,TS_3_7_1
,TS_3_8_1
,TS_3_9_1
,TS_3_10_1
,TS_3_11_1
,TS_3_12_1
,TS_4_1_1
,TS_4_2_1
,TS_4_3_1
,TS_4_4_1
,TS_4_5_1
,TS_4_6_1
,TS_4_7_1
,TS_4_8_1
,TS_4_9_1
,TS_4_10_1
,TS_4_11_1
,TS_4_12_1
,MO_LENGTH,ZL,TAU,U_SIGMA,V_SIGMA,W_SIGMA,USTAR,WD,WS,WS_MAX
,FC_SSITC_TEST,FCH4_SSITC_TEST,H_SSITC_TEST,LE_SSITC_TEST,TAU_SSITC_TEST, # End of OG names

FC_UC,FCH4_UC,TAU_UC,H_UC,LE_UC,
RSSI_77,SIG_STRENGTH_72,
DOY,HOUR,MONTH,
U_FLAG,
U,V,W,
X_OFFSET,X_PEAK,X_10,X_30,X_50,X_70,X_90,
DEW_ERA5,ST1_ERA5,ST2_ERA5,LE_ERA5,PRES_ERA5,H_ERA5,
RAD_ERA5,AIRT_ERA5,PPT_ERA5,U_ERA5,V_ERA5,VWC1_ERA5,VWC2_ERA5,
RAND_ERR_CO2_FLUX, RAND_ERR_CH4_FLUX, RAND_ERR_H2O_FLUX, RAND_ERR_TAU, RAND_ERR_LE, RAND_ERR_H


)
```


Write off final csv with Ameriflux naming convention
```{r}
siteID_i = "CA-CF3"
resolution_i = 'HH'
tsstart_i = INTERNAL$TIMESTAMP_START[1]
tsend_i   = INTERNAL$TIMESTAMP_END[nrow(INTERNAL)]

filename_i = paste(siteID_i,resolution_i,'INTERNAL',tsstart_i,tsend_i,sep = '_')
filename_i = paste("./internal/",filename_i,".csv",sep = "")

write.csv(x = INTERNAL,file = filename_i,row.names = F,na = "-9999")
```


