---
title: "Churchill Cleaning"
output: pdf_document
date: "2022-12-08"
---

# To Do


Make sure all of the timestamps are loaded
Look at roll apply command

# Loading DF's

Clear Console and add packages


# Load 

```{r, warning=FALSE}
rm(list = ls())
Sys.setenv(TZ = "UTC")

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
```



```{r, warning=FALSE}

# df = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet.dat',na.strings = c('-9999','NA','NaN','NAN','-7999'))
# 
# h = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet_until20240622.dat',skip=1 ,nrows = 0)
# dat = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet_until20240622.dat',skip=4, header = FALSE, na.strings=c('-9999','NA','NaN','NAN',"-7999"))
# 
# h2 = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet_until20240802.dat',skip=1 ,nrows = 0)
# dat2 = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet_until20240802.dat',skip=4, header = FALSE, na.strings=c('-9999','NA','NaN','NAN',"-7999"))
# 
# h3 = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet.dat',skip=1 ,nrows = 0)
# dat3 = fread('C:/Users/dtrangmoe/Documents/Churchill/raw/Churchill_AllBiomet.dat',skip=4, header = FALSE, na.strings=c('-9999','NA','NaN','NAN',"-7999"))
# 
# names(dat) = names(h)
# names(dat2) = names(h2)
# names(dat3) = names(h3)
# 
# met= dat
# met2 = dat2
# met3 = dat3
# 
# df = rbind.fill(met,met2,met3)
# 
# df = df[!duplicated(df$TIMESTAMP),]
# 
# 
# 
# #check time stamps to ensure we have a complete series
# TIMESTAMP = seq(from = min(df$TIMESTAMP), to = max(df$TIMESTAMP),by = 60*30,tz = "UTC")
# tsdf = as.data.frame(TIMESTAMP)
# 
# df = merge(tsdf,df,by = "TIMESTAMP",all = T)
# 
# 
# #na.strings not working for numbers for some reason, remove all here
# df[df == -9999] = NA
# df[df == -7999] = NA
# summary(df)


# write.csv(x = df,file = 'C:/Users/dtrangmoe/Documents/Churchill/Churchill_met_merged2024.csv',row.names = F,quote = F)

## for loading in merged file
df <- fread('C:/Users/dtrangmoe/Documents/Churchill/Churchill_met_merged2024.csv')

df <- subset(df, df$TIMESTAMP > as.POSIXct('2024-01-01'))
```


Creates a variable to input a date range for the plots in the biomet section of
cleaning code. Used to easily change date range for different data sets. 
```{r, warning=FALSE}
biomet_dates <- c('2024-01-01', '2024-09-15')
```


# Air T 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,TA_2_1_1_1_1),col='black')+
  scale_y_continuous(#limits = c(-40,40),
                     expression('Air Temperature ('*Celsius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```



#Relative Humidity 

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_19_3_1_1_1),col='black')+
  scale_y_continuous(#limits = c(20,100),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$RH_19_3_1_1_1.c <- df$RH_19_3_1_1_1
```


# Barometric Pressure 

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(#limits = c(90000,110000),
                     expression ('Barometric Pressure ('*kPa*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$PA_4_2_1_1_1.c = ifelse(df$PA_4_2_1_1_1 < 50, NA ,df$PA_4_2_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(#limits = c(0,200),
                     expression ('Barometric Pressure ('*kPa*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))



```


#Soil Heat Flux 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SHF_6_37_1_1_1,col='SHF 1'))+
  geom_point(aes(TIMESTAMP,SHF_6_37_2_1_1,col='SHF 2'))+
  scale_y_continuous(limits = c(-80,190),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','black'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$SHF_6_37_1_1_1.c <- df$SHF_6_37_1_1_1
df$SHF_6_37_2_1_1.c <- df$SHF_6_37_2_1_1
```

# Snow Depth 
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1),col='black')+
  scale_y_continuous(#limits = c(-1.5,.75),
                     expression('Snow Depth ('*m*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```


```{r, warning=FALSE}
hist(df$SD_10_99_1_1_1,breaks=100)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1),col='black')+
  scale_y_continuous(#limits = c(-1.5,.75),
                     expression('Snow Depth ('*m*')'))+
  geom_hline(yintercept = 0, color = "red")+
  geom_hline(yintercept = 0.65, color = "red")+
  geom_vline(xintercept = as.POSIXct("2024-05-10"), color = "red")

SD_10_99_1_1_1.limits=df$SD_10_99_1_1_1
SD_10_99_1_1_1.limits = ifelse(df$SD_10_99_1_1_1 < 0 | df$SD_10_99_1_1_1 > .65,NA,df$SD_10_99_1_1_1)
SD_10_99_1_1_1.limits = ifelse(df$SD_10_99_1_1_1 > 0.2 & df$TIMESTAMP > as.POSIXct('2024-05-10'),NA,SD_10_99_1_1_1.limits)
                               
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits),col='black')+
  scale_y_continuous(#limits = c(-.25,.75),
                     expression('Snow Depth ('*m*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$SD_10_99_1_1_1.c = SD_10_99_1_1_1.limits 
```

## Rolling MAD
```{r, warning=FALSE}
f = SD_10_99_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

```

```{r, warning=FALSE}

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits,col='Snow Depth'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-.1,.8))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 2

#Add clean value to dataframe (_.c)

df$SD_10_99_1_1_1.c = ifelse(abs(SD_10_99_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SD_10_99_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-0.75,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```


```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-.25,.5))+
scale_x_datetime(limits = as.POSIXct(c('2024-1-1','2024-2-26'),format="%F"))

```


# PAR 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1),col='black')+
  scale_y_continuous(limits = c(-25,2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))
```

```{r, warning=FALSE}
summary(df$PPFD_7_21_1_1_1)
# hist(df$PPFD_7_21_1_1_1,breaks=100)
# plot(df$TIMESTAMP,df$PPFD_7_21_1_1_1,ylim = c(0,1850));abline(h=1750, col= 'red');abline(h=0, col='red')
# PPFD_7_21_1_1_1.limits = replace(df$PPFD_7_21_1_1_1, df$PPFD_7_21_1_1_1 < 0 | df$PPFD_7_21_1_1_1 > 1750,NA)
# hist(PPFD_7_21_1_1_1.limits,breaks=100)
# plot(PPFD_7_21_1_1_1.limits)

df$PPFD_7_21_1_1_1.c <- df$PPFD_7_21_1_1_1
```


# PAR Reflected 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1),col='black')+
  scale_y_continuous(limits = c(-25,1600),
                     expression('PAR Reflected ('*mu*mol/m^2/s*')'))
```

```{r, warning=FALSE}
# summary(df$PPFDR_7_23_1_1_1)
# hist(df$PPFDR_7_23_1_1_1,breaks=100)
# plot(df$TIMESTAMP,df$PPFDR_7_23_1_1_1,ylim = c(0,5850));abline(h=1400, col= 'red');abline(h=-1, col='red')
# PPFDR_7_23_1_1_1.limits=df$PPFDR_7_23_1_1_1
# PPFDR_7_23_1_1_1.limits = ifelse(df$PPFDR_7_23_1_1_1 < -1 | df$PPFDR_7_23_1_1_1 > 600 & df$TIMESTAMP <= '2022-10-31',NA,df$PPFDR_7_23_1_1_1)
# hist(PPFDR_7_23_1_1_1.limits,breaks=100)
# plot(PPFDR_7_23_1_1_1.limits)

df$PPFDR_7_23_1_1_1.c <- df$PPFDR_7_23_1_1_1
```


# Net Radiation 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, RN_6_5_1_1_1),col='black')+
  scale_y_continuous(#limits = c(-125,850),
                     expression('Net Radiation ('*W/m^2*')'))
```

```{r, warning=FALSE}
# hist(df$RN_6_5_1_1_1,breaks=100)
# plot(df$TIMESTAMP,df$RN_6_5_1_1_1,ylim = c(-400,850));abline(h=835,col= 'red');abline(h=-300, col='red')
# RN_6_5_1_1_1.limits = replace(df$RN_6_5_1_1_1, df$RN_6_5_1_1_1 < -300 | df$RN_6_5_1_1_1 > 835,NA)
# hist(RN_6_5_1_1_1.limits,breaks=100)
# plot(df$TIMESTAMP,RN_6_5_1_1_1.limits)

RN_6_5_1_1_1.limits <- df$RN_6_5_1_1_1
df$RN_6_5_1_1_1.c <- df$RN_6_5_1_1_1
```

# Shortwave in 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWIN_6_10_1_1_1))+
  scale_y_continuous(#limits = c(-10,1000),
                     expression('Shortwave In ('*W/m^2*')'))
```


```{r, warning=FALSE}

# hist(df$SWIN_6_10_1_1_1,breaks=100)
# plot(df$TIMESTAMP,df$SWIN_6_10_1_1_1,ylim = c(0,1000));abline(h=900,col= 'red');abline(h=-1, col='red')
# SWIN_6_10_1_1_1.limits <- df$SWIN_6_10_1_1_1
# SWIN_6_10_1_1_1.limits[df$SWIN_6_10_1_1_1 < 0] <- 0
# hist(SWIN_6_10_1_1_1.limits,breaks=100)
# plot(df$TIMESTAMP,SWIN_6_10_1_1_1.limits)

summary(df$SWIN_6_10_1_1_1)

SWIN_6_10_1_1_1.limits <- df$SWIN_6_10_1_1_1

SWIN_6_10_1_1_1.limits[df$SWIN_6_10_1_1_1 < 0] <- 0

df$SWIN_6_10_1_1_1.c <- SWIN_6_10_1_1_1.limits


```


# Shortwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWOUT_6_11_1_1_1))+
  scale_y_continuous(limits = c(-10,750),
                     expression('Shortwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

```{r, warning=FALSE}
# hist(df$SWOUT_6_11_1_1_1,breaks=100)
# plot(df$TIMESTAMP,df$SWOUT_6_11_1_1_1,ylim = c(0,800));abline(h=700,col= 'red');abline(h=-1, col='red')

SWOUT_6_11_1_1_1.limits <- df$SWOUT_6_11_1_1_1
SWOUT_6_11_1_1_1.limits[df$SWOUT_6_11_1_1_1 < 0] <- 0

df$SWOUT_6_11_1_1_1.c <- SWOUT_6_11_1_1_1.limits
```


# Albedo 
```{r, warning=FALSE}
albedo = df$SWOUT_6_11_1_1_1.c / df$SWIN_6_10_1_1_1.c

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo))+
  scale_y_continuous(limits = c(-1,2),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

albedo.limits = replace(albedo, albedo < .05 | albedo > 1,NA)


ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo.limits))+
  scale_y_continuous(limits = c(-.5,1.5),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


```

```{r, warning=FALSE}
f = albedo.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Albedo'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 2

#Add clean value to dataframe (_.c)

df$ALB_1_1_1.c = ifelse(abs(albedo.limits - mad_filt) > (N * roll.mad),NA,albedo.limits)

#Compare cleaned vs. uncleaned


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$ALB_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,1))+
  scale_color_manual(values=c('black','red'))


```

# Longwave In 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWIN_6_14_1_1_1))+
  scale_y_continuous(limits = c(50,750),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```

```{r, warning=FALSE}
hist(df$LWIN_6_14_1_1_1,breaks=100)


df$LWIN_6_14_1_1_1.c = df$LWIN_6_14_1_1_1
```


# Longwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWOUT_6_15_1_1_1))+
  scale_y_continuous(#limits = c(150,750),
                     expression('Longwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

```{r, warning=FALSE}

hist(df$LWOUT_6_15_1_1_1,breaks=100)


df$LWOUT_6_15_1_1_1.c = df$LWOUT_6_15_1_1_1
```

# Soil Temps

#All Hummock Therms
```{r}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_4_1_1,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_2_1,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_3_1,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_4_1,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_4_5_1,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_6_1,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_7_1,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_8_1,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_9_1,color='70 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_10_1,color='80 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_11_1,color='90 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_12_1,color='1 m')) 
```
  

# All Open Water therms
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_3_1_1,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_2_1,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_3_1,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_4_1,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_3_5_1,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_6_1,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_7_1,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_8_1,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_9_1,color='70 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_10_1,color='80 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_11_1,color='90 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_12_1,color='1 m')) 
```

# Hummocks clean

```{r, warning=FALSE}

df$TS_2_38_4_1_1.c <- df$TS_2_38_4_1_1
df$TS_2_38_4_2_1.c <- df$TS_2_38_4_2_1
df$TS_2_38_4_3_1.c <- df$TS_2_38_4_3_1
df$TS_2_38_4_4_1.c <- df$TS_2_38_4_4_1
df$TS_2_38_4_5_1.c <- df$TS_2_38_4_5_1
df$TS_2_38_4_6_1.c <- df$TS_2_38_4_6_1
df$TS_2_38_4_7_1.c <- df$TS_2_38_4_7_1
df$TS_2_38_4_8_1.c <- df$TS_2_38_4_8_1
df$TS_2_38_4_9_1.c <- df$TS_2_38_4_9_1
df$TS_2_38_4_10_1.c <- df$TS_2_38_4_10_1
df$TS_2_38_4_11_1.c <- df$TS_2_38_4_11_1
df$TS_2_38_4_12_1.c <- df$TS_2_38_4_12_1

```

# Open Water clean

```{r, warning=FALSE}

df$TS_2_38_3_1_1.c <- df$TS_2_38_3_1_1
df$TS_2_38_3_2_1.c <- df$TS_2_38_3_2_1
df$TS_2_38_3_3_1.c <- df$TS_2_38_3_3_1
df$TS_2_38_3_4_1.c <- df$TS_2_38_3_4_1
df$TS_2_38_3_5_1.c <- df$TS_2_38_3_5_1
df$TS_2_38_3_6_1.c <- df$TS_2_38_3_6_1
df$TS_2_38_3_7_1.c <- df$TS_2_38_3_7_1
df$TS_2_38_3_8_1.c <- df$TS_2_38_3_8_1
df$TS_2_38_3_9_1.c <- df$TS_2_38_3_9_1
df$TS_2_38_3_10_1.c <- df$TS_2_38_3_10_1
df$TS_2_38_3_11_1.c <- df$TS_2_38_3_11_1
df$TS_2_38_3_12_1.c <- df$TS_2_38_3_12_1

```



# Save

```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/dtrangmoe/Documents/Churchill/Churchill_met_clean_2024.csv',row.names = F,quote = F)
```

