---
title: "Timestamp Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/github/churchill_cleaning_processing') #use this to set your directory
```


This file merges met and flux data, checks that timestamps are aligned, and performs any necessary adjustments. Final timezone should be in standard local time (CST in Churchill), and the solar noon should line up with the noon timestamp 

Load packages 
```{r, include=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(plotrix)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(bigleaf) # for radiation check
Sys.setenv(TZ = "UTC")
```


# Merge met and flux data

Load data
```{r}

met <- fread('./outputs/cleaning/Churchill_met_merged_2022_2025.csv')
df <- fread('./outputs/cleaning/Churchill_fluxes_merged_2022_2025.csv')

```

## Adjust flux timestamps only, merge
```{r}

df$TIMESTAMP <- df$ts
df$ts <- NULL

#Adjustment here
df$TIMESTAMP <- as.POSIXct(ifelse(df$TIMESTAMP >= as.POSIXct("2025-05-01 23:30:00") & df$TIMESTAMP <= as.POSIXct("2025-06-28 23:30:00"), df$TIMESTAMP+6*3600, df$TIMESTAMP)) 

#Merge here
df= merge(df,met,by='TIMESTAMP',all = T)

#check time stamps to ensure we have a complete series
TIMESTAMP = seq(from = min(df$TIMESTAMP), to = max(df$TIMESTAMP),by = 60*30,tz = "UTC")
tsdf = as.data.frame(TIMESTAMP)

df = merge(tsdf,df,by = "TIMESTAMP",all = T)

df = df[!duplicated(df$TIMESTAMP),]

rm(met, tsdf, TIMESTAMP)

```

## Align merged datasets here

```{r}

#adjust timezone from UTC to CST where needed
df$TIMESTAMP <- as.POSIXct(ifelse(df$TIMESTAMP <= as.POSIXct("2025-06-28 23:30:00"), df$TIMESTAMP-6*3600, df$TIMESTAMP))

#Remove problematic chunk
df <- dplyr::filter(df, !(df$TIMESTAMP >= as.POSIXct("2025-02-26 18:00:00") & df$TIMESTAMP <= as.POSIXct("2025-03-03 18:00:00")))

#Refill timestamp to ensure full timeseries
#check time stamps to ensure we have a complete series
TIMESTAMP = seq(from = min(df$TIMESTAMP), to = max(df$TIMESTAMP),by = 60*30,tz = "UTC")

tsdf = as.data.frame(TIMESTAMP)

df = merge(tsdf,df,by = "TIMESTAMP",all = T)


df = df[!duplicated(df$TIMESTAMP),]


```



# Radiation timestamp alignment check

Create potential radiation dataset
```{r}

mindate = as.POSIXct(min(df$TIMESTAMP), tz = "UTC")
maxdate = as.POSIXct(max(df$TIMESTAMP), tz = "UTC")
  
TIMESTAMP <- as.POSIXct(seq(from = mindate,
                           to = maxdate,
                           by = 60*30),'yyyy-mm-dd HH:MM:SS', tz = 'UTC')
JD <- as.numeric(format(seq(from = mindate,
                           to = maxdate,
                           by = 60*30),'%j'))
h <- as.numeric(format(seq(from = mindate,
                           to = maxdate,
                           by = 60*30),'%H'))
m <- as.numeric(format(seq(from = mindate,
                          to = maxdate,
                          by = 60*30),'%M'))
H <- h+ifelse(m == 30,0.5,0)

rpot <- potential.radiation(doy = JD,hour = H,latDeg = 59,longDeg = -94,timezone = -6,useSolartime = T)*1.1


rpot <- as.data.frame(cbind(TIMESTAMP, rpot))


df <- merge(df, rpot, by = 'TIMESTAMP', all = T)
```


Preliminary checks
```{r}

df$radflag <- ifelse(df$SWIN_6_10_1_1_1 > df$rpot, 1, 0)

#Look for pionts of mismatch - things above the 1:1 line are weird!!

ggplot(data = df)+
  geom_point(aes(x = rpot, y = SWIN_6_10_1_1_1, color = radflag))+
  geom_abline(yint = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(0, 1000))+
  scale_y_continuous(limits = c(0, 1000))

## A quick test for finding strange points in previous plots
#test <- subset(df, rpot < SWIN_6_10_1_1_1 & SWIN_6_10_1_1_1 > 500)

## Check that solar noon makes sense

ggplot(data = df)+
    geom_vline(xintercept = as.POSIXct("2024-08-12 12:00:00"))+
    geom_point(aes(x = TIMESTAMP, y = SWIN_6_10_1_1_1, color = radflag)) +
    geom_line(aes(x = TIMESTAMP, y = rpot), color = "blue")+
    scale_x_datetime(limits = as.POSIXct(c("2024-08-08","2024-08-20")))+
    labs(x = "Time", y = "Rad")+
    theme_minimal()
  
  
```


## Create and display a plot of every two week period

### Create function
```{r}
generate_two_week_plots_rad <- function(df, timestamp_col, value_col) {
  
  #Determine the overall date range
  start_datetime <- min(df[[timestamp_col]])
  end_datetime <- max(df[[timestamp_col]])

  #Set the interval length: 14 days (in seconds)
  interval_seconds <- 14 * 24 * 3600

  #Initialize loop variables
  current_start <- start_datetime
  plot_count <- 1
  
  # The base plot object (data and aesthetics are defined once)
  base_plot <- ggplot(data = df)+
    aes(x = .data[[timestamp_col]], y = .data[[value_col]]) +
    geom_point(aes(x = .data[[timestamp_col]], y = .data[[value_col]], color = .data[["radflag"]])) +
    geom_line(aes(x = .data[[timestamp_col]], y = .data[["rpot"]]), color = "blue")+
    labs(x = "Time", y = value_col) +
    theme_minimal()
  
  #Loop through the time series in 14-day increments
  while (current_start < end_datetime) {
    
    #Calculate the end time for the current 14-day period
    current_end <- current_start + interval_seconds
    
    #Ensure the last plot doesn't go beyond the series end time
    if (current_end > end_datetime) {
      current_end <- end_datetime
    }
    
    #Define the title based on the limits being plotted
    plot_title <- paste0(
      "Data from ", 
      format(current_start, "%Y-%m-%d"), 
      " to ", 
      format(current_end, "%Y-%m-%d")
    )
    
    #Build the plot with dynamic limits
    p <- base_plot +
      scale_x_datetime(
        limits = c(current_start, current_end),
        date_breaks = "2 day", 
        date_labels = "%b %d"
      ) +
      ggtitle(plot_title)
    
    #Save the plot object to the global environment
    plot_name <- paste0("rad_plot_", plot_count)
    assign(plot_name, p, envir = .GlobalEnv)
    
    #Move to the start of the next 14-day interval
    current_start <- current_start + interval_seconds
    plot_count <- plot_count + 1
  }
}

generate_two_week_plots_rad(df, "TIMESTAMP","SWIN_6_10_1_1_1")
```


### View all plots
```{r}
view_all_generated_plots_rad <- function(pattern = "^rad_plot_") {
  
  #Identify all objects in the global environment that start with 'plot_'
  plot_names <- ls(envir = .GlobalEnv, pattern = pattern)
  
  #Extract the number for numeric sorting
  plot_numbers <- as.numeric(gsub("\\D", "", plot_names))
  
  #Get the correct sorting order
  correct_order_indices <- order(plot_numbers)
  
  #Reorder the plot names based on the correct numeric indices
  sorted_plot_names <- plot_names[correct_order_indices]
  message("Press [Enter] to display the next plot...")
  
  #Loop through each plot name
  for (name in sorted_plot_names) {
    
    #Retrieve the object (the ggplot object) by its name (a string)
    p <- get(name, envir = .GlobalEnv)
    
    #Print the plot to the RStudio plot pane
    print(p)

    readline(prompt = paste("Displaying:", name, "- Press [Enter] for next plot."))
  }
  
  message("All plots have been displayed.")
}


view_all_generated_plots_rad()
```




# Flux vs. met alignment check - uses HMP and sonic temperature

One to one plot for initial check
```{r}

ggplot(data = df)+
  geom_point(aes(x = TA_2_1_1_1_1, y = sonic_temperature-273.15, color = TIMESTAMP))+
  geom_abline(yintercept = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(-43, 35))+
  scale_y_continuous(limits = c(-43, 35))

  
```


## Create and display a plot of every two week period

### Create function
```{r}
generate_two_week_plots_temp <- function(df, timestamp_col, value_col_1, value_col_2) {
  
  #Determine the overall date range
  start_datetime <- min(df[[timestamp_col]])
  end_datetime <- max(df[[timestamp_col]])

  #Set the interval length: 14 days (in seconds)
  interval_seconds <- 14 * 24 * 3600

  #Initialize loop variables
  current_start <- start_datetime
  plot_count <- 1
  
  # The base plot object (data and aesthetics are defined once)
  base_plot <- ggplot(data = df)+
    geom_point(aes(x = .data[[timestamp_col]], y = .data[[value_col_1]])) +
    geom_point(aes(x = .data[[timestamp_col]], y = .data[[value_col_2]]-273.15), color = "blue")+
    labs(x = "Time", y = "Temp") +
    theme_minimal()
  
  #Loop through the time series in 14-day increments
  while (current_start < end_datetime) {
    
    #Calculate the end time for the current 14-day period
    current_end <- current_start + interval_seconds
    
    #Ensure the last plot doesn't go beyond the series end time
    if (current_end > end_datetime) {
      current_end <- end_datetime
    }
    
    #Define the title based on the limits being plotted
    plot_title <- paste0(
      "Data from ", 
      format(current_start, "%Y-%m-%d"), 
      " to ", 
      format(current_end, "%Y-%m-%d")
    )
    
    #Build the plot with dynamic limits
    p <- base_plot +
      scale_x_datetime(
        limits = c(current_start, current_end),
        date_breaks = "2 day", 
        date_labels = "%b %d"
      ) +
      ggtitle(plot_title)
    
    #Save the plot object to the global environment
    plot_name <- paste0("temp_plot_", plot_count)
    assign(plot_name, p, envir = .GlobalEnv)
    
    #Move to the start of the next 14-day interval
    current_start <- current_start + interval_seconds
    plot_count <- plot_count + 1
  }
}

generate_two_week_plots_temp(df, "TIMESTAMP","TA_2_1_1_1_1", "sonic_temperature")
```


### View all plots
```{r}
view_all_generated_plots_temp <- function(pattern = "^temp_plot_") {
  
  #Identify all objects in the global environment that start with 'plot_'
  plot_names <- ls(envir = .GlobalEnv, pattern = pattern)
  
  #Extract the number for numeric sorting
  plot_numbers <- as.numeric(gsub("\\D", "", plot_names))
  
  #Get the correct sorting order
  correct_order_indices <- order(plot_numbers)
  
  #Reorder the plot names based on the correct numeric indices
  sorted_plot_names <- plot_names[correct_order_indices]
  message("Press [Enter] to display the next plot...")
  
  #Loop through each plot name
  for (name in sorted_plot_names) {
    
    #Retrieve the object (the ggplot object) by its name (a string)
    p <- get(name, envir = .GlobalEnv)
    
    #Print the plot to the RStudio plot pane
    print(p)

    readline(prompt = paste("Displaying:", name, "- Press [Enter] for next plot."))
  }
  
  message("All plots have been displayed.")
}


# view_all_generated_plots_temp()
```


# Diurnal Fluxes

set hour and month vectors to be able to take the averages

```{r, warning=FALSE}
df$hour = as.numeric(format(df$TIMESTAMP,'%H'))
df$month = as.numeric(format(df$TIMESTAMP,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux,ch4_flux,LE,H, RN_6_5_1_1_1,hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

## NEE

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux_fn1,
                  ymax = co2_flux_fn1 + co2_flux_fn2,
                  ymin = co2_flux_fn1 - co2_flux_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
levels(diel$month)
```

## CH4

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux_fn1,
                  ymax = ch4_flux_fn1 + ch4_flux_fn2,
                  ymin = ch4_flux_fn1 - ch4_flux_fn2),
              alpha= 0.5)+
  facet_wrap(~month)

ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux_fn1*43.2),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux_fn1*43.2,
                  ymax = ch4_flux_fn1*43.2 + ch4_flux_fn2*43.2,
                  ymin = ch4_flux_fn1*43.2 - ch4_flux_fn2*43.2),
              alpha= 0.5)+
  scale_y_continuous(limits = c(-1,6))+
  facet_wrap(~month)
```

## H

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = H_fn1,
                  ymax = H_fn1 + H_fn2,
                  ymin = H_fn1 - H_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```

## LE

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = LE_fn1,
                  ymax = LE_fn1 + LE_fn2,
                  ymin = LE_fn1 - LE_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```


## Net Rad

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,RN_6_5_1_1_1_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = RN_6_5_1_1_1_fn1,
                  ymax = RN_6_5_1_1_1_fn1 + RN_6_5_1_1_1_fn2,
                  ymin = RN_6_5_1_1_1_fn1 - RN_6_5_1_1_1_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```




# A zoom in on some known problematic periods: 

February 26th to March 3rd, 2025: both flux and met misaligned, chopped data

```{r}

ggplot(data = df)+
  geom_line(aes(x = TIMESTAMP, y = rpot), color = "blue2")+
  geom_line(aes(x = TIMESTAMP, y = SWIN_6_10_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-02-20", "2025-03-08")))+
  geom_vline(xintercept = as.POSIXct("2025-02-26 12:00"))+
  geom_vline(xintercept = as.POSIXct("2025-03-03 12:00"))

```

April 28th to June 28th, 2025: Flux and met timestamps not lining up

```{r}

ggplot(data = df)+
  geom_line(aes(x = TIMESTAMP, y = sonic_temperature-273.15), color = "blue2")+
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-04-26", "2025-07-01")))

```

Timestamp change for whole system on June 28th, 2025

```{r}

ggplot(data = df)+
  geom_line(aes(x = TIMESTAMP, y = rpot), color = "blue2")+
  geom_line(aes(x = TIMESTAMP, y = SWIN_6_10_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-06-20", "2025-06-30")))+
  geom_vline(xintercept = as.POSIXct("2025-06-24 12:00"))

```


# Write aligned CSV file
```{r}

write.csv(x = df,file = './outputs/cleaning/Churchill_met_flux_merged_aligned_2025.csv',row.names = F,quote = F)

```



