---
title: "Timestamp Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/github/churchill_cleaning_processing') #use this to set your directory
```


This file merges met and flux data, checks that timestamps are aligned, and performs any necessary adjustments

Load packages 
```{r, include=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(plotrix)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(bigleaf) # for radiation check
```


# Merge met and flux data

Load data
```{r}

met <- fread('./outputs/cleaning/Churchill_met_merged_2025.csv')
df <- fread('./outputs/cleaning/Churchill_fluxes_merged_2025.csv')

```

## Adjust flux timestamps only, merge
```{r}

df$TIMESTAMP = df$ts

#Adjustment here
df$TIMESTAMP <- as.POSIXct(ifelse(df$TIMESTAMP >= as.POSIXct("2025-05-01 23:30:00") & df$TIMESTAMP <= as.POSIXct("2025-06-28 23:30:00"), df$TIMESTAMP+6*3600, df$TIMESTAMP)) 

#Merge here
df= merge(df,met,by='TIMESTAMP',all = T)

#check time stamps to ensure we have a complete series
TIMESTAMP = seq(from = min(df$TIMESTAMP), to = max(df$TIMESTAMP),by = 60*30,tz = "UTC")
tsdf = as.data.frame(TIMESTAMP)

df = merge(tsdf,df,by = "TIMESTAMP",all = T)

rm(met, tsdf)

```

## Align merged datasets here

```{r}

#adjust timezone from UTC to CST

df$TIMESTAMP <- as.POSIXct(ifelse(df$TIMESTAMP <= as.POSIXct("2025-06-28 23:30:00"), df$TIMESTAMP-6*3600, df$TIMESTAMP)) 
#Remove problematic chunk
df <- dplyr::filter(df, !(df$TIMESTAMP >= as.POSIXct("2025-02-26 18:00:00") & df$TIMESTAMP <= as.POSIXct("2025-03-03 18:00:00")))

#Refill timestamp to ensure full timeseries
#check time stamps to ensure we have a complete series
TIMESTAMP = seq(from = min(df$TIMESTAMP), to = max(df$TIMESTAMP),by = 60*30,tz = "UTC")
tsdf = as.data.frame(TIMESTAMP)

df = merge(tsdf,df,by = "TIMESTAMP",all = T)


```



# Radiation timestamp alignment check

Create potential radiation dataset
```{r}
TIMESTAMP <- as.POSIXct(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                           to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                           by = 60*30),'yyyy-mm-dd HH:MM:SS', tz = 'UTC')

JD <- as.numeric(format(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                           to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                           by = 60*30),'%j'))
h <- as.numeric(format(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                           to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                           by = 60*30),'%H'))
m <- as.numeric(format(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                          to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                          by = 60*30),'%M'))
H <- h+ifelse(m == 30,0.5,0)

rpot <- potential.radiation(doy = JD,hour = H,latDeg = 59,longDeg = -94,timezone = -6,useSolartime = F)*1.1

rpot <- as.data.frame(cbind(TIMESTAMP, rpot))

df <- merge(df, rpot, by = 'TIMESTAMP', all = T)
```


One to one plot for check
```{r}

df$radflag <- ifelse(df$SWIN_6_10_1_1_1 > df$rpot, 1, 0)

## For finding strange points
#test <- subset(df, rpot < SWIN_6_10_1_1_1 & SWIN_6_10_1_1_1 > 500)

ggplot(data = df)+
  geom_point(aes(x = rpot, y = SWIN_6_10_1_1_1, color = radflag))+
  geom_abline(yint = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(0, 1000))+
  scale_y_continuous(limits = c(0, 1000))

  
  
```


## Create and display a plot of every two week period

### Create function
```{r}
generate_two_week_plots_rad <- function(df, timestamp_col, value_col) {
  
  #Determine the overall date range
  start_datetime <- min(df[[timestamp_col]])
  end_datetime <- max(df[[timestamp_col]])

  #Set the interval length: 14 days (in seconds)
  interval_seconds <- 14 * 24 * 3600

  #Initialize loop variables
  current_start <- start_datetime
  plot_count <- 1
  
  # The base plot object (data and aesthetics are defined once)
  base_plot <- ggplot(data = df)+
    aes(x = .data[[timestamp_col]], y = .data[[value_col]]) +
    geom_point(aes(x = .data[[timestamp_col]], y = .data[[value_col]], color = .data[["radflag"]])) +
    geom_line(aes(x = .data[[timestamp_col]], y = .data[["rpot"]]), color = "blue")+
    labs(x = "Time", y = value_col) +
    theme_minimal()
  
  #Loop through the time series in 14-day increments
  while (current_start < end_datetime) {
    
    #Calculate the end time for the current 14-day period
    current_end <- current_start + interval_seconds
    
    #Ensure the last plot doesn't go beyond the series end time
    if (current_end > end_datetime) {
      current_end <- end_datetime
    }
    
    #Define the title based on the limits being plotted
    plot_title <- paste0(
      "Data from ", 
      format(current_start, "%Y-%m-%d"), 
      " to ", 
      format(current_end, "%Y-%m-%d")
    )
    
    #Build the plot with dynamic limits
    p <- base_plot +
      scale_x_datetime(
        limits = c(current_start, current_end),
        date_breaks = "2 day", 
        date_labels = "%b %d"
      ) +
      ggtitle(plot_title)
    
    #Save the plot object to the global environment
    plot_name <- paste0("rad_plot_", plot_count)
    assign(plot_name, p, envir = .GlobalEnv)
    
    #Move to the start of the next 14-day interval
    current_start <- current_start + interval_seconds
    plot_count <- plot_count + 1
  }
}

generate_two_week_plots_rad(df, "TIMESTAMP","SWIN_6_10_1_1_1")
```


### View all plots
```{r}
view_all_generated_plots_rad <- function(pattern = "^rad_plot_") {
  
  #Identify all objects in the global environment that start with 'plot_'
  plot_names <- ls(envir = .GlobalEnv, pattern = pattern)
  
  #Extract the number for numeric sorting
  plot_numbers <- as.numeric(gsub("\\D", "", plot_names))
  
  #Get the correct sorting order
  correct_order_indices <- order(plot_numbers)
  
  #Reorder the plot names based on the correct numeric indices
  sorted_plot_names <- plot_names[correct_order_indices]
  message("Press [Enter] to display the next plot...")
  
  #Loop through each plot name
  for (name in sorted_plot_names) {
    
    #Retrieve the object (the ggplot object) by its name (a string)
    p <- get(name, envir = .GlobalEnv)
    
    #Print the plot to the RStudio plot pane
    print(p)

    readline(prompt = paste("Displaying:", name, "- Press [Enter] for next plot."))
  }
  
  message("All plots have been displayed.")
}


view_all_generated_plots_rad()




```




# Flux vs. met alignment check - uses HMP and sonic temperature

One to one plot for initial check
```{r}

ggplot(data = df)+
  geom_point(aes(x = TA_2_1_1_1_1, y = sonic_temperature-273.15, color = TIMESTAMP))+
  geom_abline(yint = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(-43, 35))+
  scale_y_continuous(limits = c(-43, 35))

  
```


## Create and display a plot of every two week period

### Create function
```{r}
generate_two_week_plots_temp <- function(df, timestamp_col, value_col_1, value_col_2) {
  
  #Determine the overall date range
  start_datetime <- min(df[[timestamp_col]])
  end_datetime <- max(df[[timestamp_col]])

  #Set the interval length: 14 days (in seconds)
  interval_seconds <- 14 * 24 * 3600

  #Initialize loop variables
  current_start <- start_datetime
  plot_count <- 1
  
  # The base plot object (data and aesthetics are defined once)
  base_plot <- ggplot(data = df)+
    geom_point(aes(x = .data[[timestamp_col]], y = .data[[value_col_1]])) +
    geom_point(aes(x = .data[[timestamp_col]], y = .data[[value_col_2]]-273.15), color = "blue")+
    labs(x = "Time", y = "Temp") +
    theme_minimal()
  
  #Loop through the time series in 14-day increments
  while (current_start < end_datetime) {
    
    #Calculate the end time for the current 14-day period
    current_end <- current_start + interval_seconds
    
    #Ensure the last plot doesn't go beyond the series end time
    if (current_end > end_datetime) {
      current_end <- end_datetime
    }
    
    #Define the title based on the limits being plotted
    plot_title <- paste0(
      "Data from ", 
      format(current_start, "%Y-%m-%d"), 
      " to ", 
      format(current_end, "%Y-%m-%d")
    )
    
    #Build the plot with dynamic limits
    p <- base_plot +
      scale_x_datetime(
        limits = c(current_start, current_end),
        date_breaks = "2 day", 
        date_labels = "%b %d"
      ) +
      ggtitle(plot_title)
    
    #Save the plot object to the global environment
    plot_name <- paste0("temp_plot_", plot_count)
    assign(plot_name, p, envir = .GlobalEnv)
    
    #Move to the start of the next 14-day interval
    current_start <- current_start + interval_seconds
    plot_count <- plot_count + 1
  }
}

generate_two_week_plots_temp(df, "TIMESTAMP","TA_2_1_1_1_1", "sonic_temperature")
```


### View all plots
```{r}
view_all_generated_plots_temp <- function(pattern = "^temp_plot_") {
  
  #Identify all objects in the global environment that start with 'plot_'
  plot_names <- ls(envir = .GlobalEnv, pattern = pattern)
  
  #Extract the number for numeric sorting
  plot_numbers <- as.numeric(gsub("\\D", "", plot_names))
  
  #Get the correct sorting order
  correct_order_indices <- order(plot_numbers)
  
  #Reorder the plot names based on the correct numeric indices
  sorted_plot_names <- plot_names[correct_order_indices]
  message("Press [Enter] to display the next plot...")
  
  #Loop through each plot name
  for (name in sorted_plot_names) {
    
    #Retrieve the object (the ggplot object) by its name (a string)
    p <- get(name, envir = .GlobalEnv)
    
    #Print the plot to the RStudio plot pane
    print(p)

    readline(prompt = paste("Displaying:", name, "- Press [Enter] for next plot."))
  }
  
  message("All plots have been displayed.")
}


view_all_generated_plots_temp()




```

# Add diurnals here too




# A zoom in on some known problematic periods: 

February 26th to March 3rd, 2025: both flux and met misaligned, chopped data

```{r}

ggplot(data = df)+
  geom_line(aes(x = TIMESTAMP, y = rpot), color = "blue2")+
  geom_line(aes(x = TIMESTAMP, y = SWIN_6_10_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-02-20", "2025-03-08")))+
  geom_vline(xintercept = as.POSIXct("2025-02-26 12:00"))+
  geom_vline(xintercept = as.POSIXct("2025-03-03 12:00"))

```

April 28th to June 28th, 2025: Flux and met timestamps not lining up

```{r}

ggplot(data = df)+
  geom_line(aes(x = TIMESTAMP, y = sonic_temperature-273.15), color = "blue2")+
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-04-26", "2025-07-01")))

```

Timestamp change for whole system on June 28th, 2025

```{r}

ggplot(data = df)+
  geom_line(aes(x = TIMESTAMP, y = rpot), color = "blue2")+
  geom_line(aes(x = TIMESTAMP, y = SWIN_6_10_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-06-20", "2025-06-30")))+
  geom_vline(xintercept = as.POSIXct("2025-06-24 08:00"))

```


# Write aligned CSV file
```{r}

write.csv(x = df,file = './outputs/cleaning/Churchill_met_flux_merged_aligned_2025.csv',row.names = F,quote = F)

```



