---
title: "3_churchill_flux_cleaning"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

# Flux Cleaning

```{r, warning=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork)
```

Load in cleaned met data and flux data

```{r warning=FALSE}
met = fread('C:/Users/dtrangmoe/Documents/sites/churchill/data/Churchill_met_clean_2025.csv')
df = fread('C:/Users/dtrangmoe/Documents/sites/churchill/data/Churchill_fluxes_merged_2025.csv')
# df = fread('C:/Users/karndt.WHRC/Desktop/sites/churchill/data/Churchill_fluxes_merged_2022_08_to_2024_10.csv')

df$TIMESTAMP = df$ts

df= merge(df,met,by='TIMESTAMP',all = T)

#check time stamps to ensure we have a complete series
TIMESTAMP = seq(from = min(df$TIMESTAMP), to = max(df$TIMESTAMP),by = 60*30,tz = "UTC")
tsdf = as.data.frame(TIMESTAMP)

df = merge(tsdf,df,by = "TIMESTAMP",all = T)
```


Creates a variable to input a date range for the plots in the flux section of
cleaning code. Used to easily change date range for different data sets. 
```{r, warning=FALSE}
flux_dates <- c('2025-01-01', '2025-08-31')
```


# Initial Clean

## EP QC

filter by the eddypro flags and create new variable _.qc

```{r, warning=FALSE}
Tau.qc      = ifelse(df$qc_Tau == 2,1,0)
co2_flux.qc = ifelse(df$qc_co2_flux == 2,1,0)
ch4_flux.qc = ifelse(df$qc_ch4_flux == 2,1,0)
LE.qc       = ifelse(df$qc_LE == 2,1,0)
H.qc        = ifelse(df$qc_H == 2,1,0)
```

Clean some data based on instrument diagnostics
```{r}
signal.threshold.co2 = ifelse(df$co2_signal_strength_7200_mean >= 75,0,1)
signal.threshold.h2o = ifelse(df$h2o_signal_strength_7200_mean >= 75,0,1)
signal.threshold.ch4 = ifelse(df$rssi_77_mean >= 10,0,1)

ggplot(data = df)+
  geom_point(aes(ts,co2_flux,color=signal.threshold.co2))+
  scale_y_continuous(limits = c(-20,20))

ggplot(data = df)+
  geom_point(aes(ts,ch4_flux,color=signal.threshold.ch4))+
  scale_y_continuous(limits = c(-0.5,0.25))

ggplot(data = df)+
  geom_point(aes(ts,h2o_flux,color=signal.threshold.h2o))+
  scale_y_continuous(limits = c(-5,10))

ggplot(data = df)+
  geom_point(aes(ts,LE,color=signal.threshold.h2o))+
  scale_y_continuous(limits = c(-200,500))
```


## Clear Outliers

look for absolute outliers and manually set some absolute limits to remove crazy data

### Tau

Plot Tau Histogram

```{r, warning=FALSE}
hist(df$Tau,breaks=100)
```

Cut the crazy data and create new variable (Tau.limits)

```{r, warning=FALSE}

Tau.limits = df$Tau
Tau.limits = ifelse(df$Tau < -0.8 | df$Tau > .1,1,0)

hist(Tau.limits,breaks=100)
```

### NEE

Plot NEE and what we might clean

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(x = TIMESTAMP, y = co2_flux))+
  geom_hline(yintercept = c(-15,8))

#This filter removes points outside of absolute limits and high uptake, low light points
co2_flux.limits = ifelse(df$co2_flux > 8 | df$co2_flux < -15 | 
                           (df$co2_flux < -5 & df$PPFD_7_21_1_1_1.c < 150),1,0)
```



### CH4

Plot CH4 and what we might clean

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,ch4_flux))+
  scale_y_continuous(limits = c(-1,1))+
  geom_hline(yintercept = c(-0.15,0.28))

ch4_flux.limits =ifelse(df$ch4_flux < -0.15 | df$ch4_flux > 0.28,1,0)
```


### H

Plot H and what we might clean

Clean based on graphs, create new variable (H.limits), and see cleaned product

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,H))+
  scale_y_continuous(limits = c(-200,500))+
  geom_hline(yintercept = c(-200,300))

H.limits =ifelse(df$H < -200 | df$H > 300,1,0)
```

### LE

Plot LE Histogram and what we might clean

Clean based on graphs, create new variable (H.limits), and see cleaned product

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(ts,LE))+
  scale_y_continuous(limits = c(-200,500))+
  geom_hline(yintercept = c(-50,450))

LE.limits =ifelse(df$LE < -50 | df$LE > 450,1,0)
```

## Plot abs. limits cleaning 
```{r}
ggplot(data = df)+
  geom_point(aes(ts,Tau,color=Tau.limits))+
  scale_y_continuous(limits = c(-1.5, 0.5))

ggplot(data = df)+
  geom_point(aes(ts,co2_flux,color=co2_flux.limits))+
  scale_y_continuous(limits = c(-35,60))

ggplot(data = df)+
  geom_point(aes(ts,ch4_flux,color=ch4_flux.limits))+
  scale_y_continuous(limits = c(-0.6,0.4))

ggplot(data = df)+
  geom_point(aes(ts,H,color=H.limits))+
  scale_y_continuous(limits = c(-215,690))

ggplot(data = df)+
  geom_point(aes(ts,LE,color=LE.limits))+
  scale_y_continuous(limits = c(-100,1100))

```

## USTAR

use night-time only flux values and plot Ustar based on data drop off

```{r, warning=FALSE}
clean.co2 = ifelse(co2_flux.limits == 1 |
                   co2_flux.qc == 2 |
                   signal.threshold.co2 == 1,NA,df$co2_flux)

df$nightCO2 = clean.co2
df$nightCO2 = replace(df$nightCO2,df$SWIN_6_10_1_1_1 > 10,NA)
1/10^9

Uthreshold=0.06
ggplot(data = df,aes(`u*`,nightCO2))+
  ylab(expression(paste("Flux (g-C", ~CO[2], ~"m",""^"-2","d",""^"-1",")")))+
  geom_point()+xlab("U*")+
  scale_x_continuous(limits = c(0,1))+
  scale_y_continuous(limits = c(-10,10))+
  geom_vline(xintercept = Uthreshold,col='red')
```

pick threshold and filter based on plots above, I liked .06


created flag to indicate where u* values are below our threshold- makes cleaning with u* optional but easy when using cleaned data sets
```{r, warning=FALSE}
df$u_flag = ifelse(df$`u*` < Uthreshold,1,0)
```

## Combine Cleaning

investigate the previous limits and combine all to create a new variable (clean), plot to see difference

```{r, warning=FALSE}
co2fluxclean = ifelse(co2_flux.qc == 2 | 
                      co2_flux.limits == 1 | 
                      signal.threshold.co2 == 1,NA,df$co2_flux)

ch4fluxclean = ifelse(ch4_flux.qc == 2 | 
                      ch4_flux.limits == 1 |
                      signal.threshold.ch4 == 1,NA,df$ch4_flux)

Hclean = ifelse(H.qc == 2 | 
                H.limits == 1,NA,df$H)

LEclean = ifelse(LE.qc == 2 | 
                 LE.limits == 1 |
                 signal.threshold.h2o == 1,NA,df$LE)

Tauclean = ifelse(Tau.qc == 2 | 
                  Tau.limits == 1,NA,df$Tau)

plot(df$ts,co2fluxclean)
plot(df$ts,ch4fluxclean)
plot(df$ts,Hclean)
plot(df$ts,LEclean)
plot(df$ts,Tauclean)
```

Add cleaned tau to dataframe (no MAD filter)
```{r, warning=FALSE}
df$Tau.c = Tauclean
```


# MAD Filter

Now, Spike filtering on half-hourly fluxes. For this type of data, filters based on median rather than std perform better. Use Unsymmetric Distributions and double MAD -MAD=Median Absolute Deviation for more info see link below <https://eurekastatistics.com/using-the-median-absolute-deviation-to-find-outliers/>

## NEE
```{r, warning=FALSE}
f = co2fluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2fluxclean,col='CO2 flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-10,10))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```

now filter the data based on this signal

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4

#Add clean value to dataframe (_.c)

df$co2_flux.c = ifelse(abs(co2fluxclean - Flux_filt) > (N * roll.mad),NA,co2fluxclean)

#Compare cleaned vs. uncleaned
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux),col='red')+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
#  scale_y_continuous(limits=c(-15,15))+
#  scale_x_datetime(limits = as.POSIXct(c("2022-07-01","2022-09-15")))
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))
```
See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,co2fluxclean),col='red')+
  geom_point(aes(ts,co2_flux.c),col='black')+
  scale_y_continuous(limits = c(-40,40))+
  scale_x_datetime(limits = as.POSIXct(c('2025-08-03','2025-08-10'),format="%F"))+
  geom_line(aes(x = ts, y = PPFD_7_21_1_1_1.c/5000))
```

## CH4
```{r, warning=FALSE}
 #apply the moving window filter
f = ch4fluxclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,ch4fluxclean,col='CH4 flux'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-.25,.3))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```

adjust this (N) to tweak how many MADs to be away from the norm, CH4 deserves more because of it's nature, add clean value to the dataframe (_.c) and compare cleaned vs. uncleaned


```{r, warning=FALSE}
N = 7

df$ch4_flux.c = ifelse(abs(ch4fluxclean - Flux_filt) > (N * roll.mad),NA,ch4fluxclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,ch4_flux.c,col='cleaned'))+
  scale_y_continuous(limits = c(-.25,.3))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
CH4Filter = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(df$ts,ch4fluxclean),col='red')+
  geom_point(aes(df$ts,ch4_flux.c),col='black')+
  scale_y_continuous(limits = c(-.1,.5))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

CH4RSSI = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_line(aes(x=ts,y=rssi_77_mean))+
  scale_y_continuous(limits = c(-1,60))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

CH4RSSI = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_line(aes(x=ts,y=rssi_77_mean))+
  scale_y_continuous(limits = c(-1,60))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

#added co2 flux to compare co2/ch4 data coverage
CO2FLUX = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=ts,y=co2_flux))+
  scale_y_continuous(limits = c(-10,10))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

CH4_FALLSOILTCOMP = plot_grid(CH4Filter,CH4RSSI,CO2FLUX,nrow=3,align = 'v')
CH4_FALLSOILTCOMP

```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(ts,ch4fluxclean),col='red')+
  geom_point(aes(ts,ch4_flux.c),col='black')+
  scale_y_continuous(limits = c(-0.6,0.6))+
  scale_x_datetime(limits = as.POSIXct(c('2025-04-03','2025-08-10'),format="%F"))+
  geom_line(aes(x = ts, y = PPFD_7_21_1_1_1.c/100000))
```


## H
```{r, warning=FALSE}
# apply the moving window filter
f = Hclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,Hclean,col='H'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-180,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
```

Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm, add clean value to dataframe (_.c) and Compare Clean vs. Uncleaned

```{r, warning=FALSE}
N = 3

df$H.c = ifelse(abs(Hclean - Flux_filt) > (N * roll.mad),NA,Hclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Hclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,H.c,col='cleaned'))+
  scale_y_continuous(limits=c(-150,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,Hclean),col='red')+
  geom_point(aes(df$ts,H.c),col='black')+
  scale_y_continuous(limits = c(-100,100))+
  scale_x_datetime(limits = as.POSIXct(c('2025-1-19','2025-2-24')))
```

## LE

```{r, warning=FALSE}
# apply the moving window filter
f = LEclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LEclean,col='LE'))+
  geom_line(aes(ts,Flux_filt,col='Filter'))+
  geom_line(aes(ts,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-50,400))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
```

Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm

```{r, warning=FALSE}
N = 6

df$LE.c = ifelse(abs(LEclean - Flux_filt) > (N * roll.mad),NA,LEclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LEclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,LE.c,col='cleaned'))+
  scale_y_continuous(limits=c(-100,400))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$ts,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$ts,LEclean),col='red')+
  geom_point(aes(df$ts,LE.c),col='black')+
  scale_y_continuous(limits = c(-20,20))+
  scale_x_datetime(limits = as.POSIXct(c('2025-01-20','2025-2-15')))
```

# Main Plots

```{r, warning=FALSE}
le <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,LE,col='Filt.'))+
  geom_point(aes(ts,LE.c,col='clean'))+
  scale_y_continuous(expression('LE ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))
  

h <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,H,col='Filt.'))+
  geom_point(aes(ts,H.c,col='clean'))+
  scale_y_continuous(expression('H ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))

co2 <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,co2_flux,col='Filt.'))+
  geom_point(aes(ts,co2_flux.c,col='clean'))+
  scale_y_continuous (expression('NEE ('*mu*mol~m^-2~s^-1*')'),
                      limits = c(-20,20))+
  scale_color_manual(values = c('black','red'))

ch4 <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(ts,ch4_flux*43.2,col='Filt.'))+
  geom_point(aes(ts,ch4_flux.c*43.2,col='clean'))+
  scale_y_continuous(expression(CH[4]~'flux ('*mu*mol~m^-2~s^-1*')'),
                     limits = c(-3,8))+
  scale_color_manual(values = c('black','red'))



png(filename = './mainplotsflux.png',width = 12,height = 8,units = 'in',res = 2000)
co2 / ch4  + plot_layout(guides = "collect", axes = "collect")
dev.off()


png(filename = './mainplotseb.png',width = 12,height = 8,units = 'in',res = 2000)
le / h  + plot_layout(guides = "collect", axes = "collect")
dev.off()

```


## Energy Balance

combine energy fluxes by met and flux components

```{r}
df$met = (df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c) - (df$LWOUT_6_15_1_1_1.c + df$SWOUT_6_11_1_1_1.c)
df$flux = df$H.c + df$LE.c

plot(df$met, df$flux)

ggplot(data = df)+
  geom_point(aes(x = met, y = flux))+
  geom_abline(aes(slope = 1, intercept = 1))+
  scale_x_continuous(limits = c(-100, 300))+
  scale_y_continuous(limits = c(-100, 300))

```

# Diurnal Fluxes

set hour and month vectors to be able to take the averages

```{r, warning=FALSE}
df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c,hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

## NEE

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
levels(diel$month)
```

## CH4

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)

ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1*43.2),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1*43.2,
                  ymax = ch4_flux.c_fn1*43.2 + ch4_flux.c_fn2*43.2,
                  ymin = ch4_flux.c_fn1*43.2 - ch4_flux.c_fn2*43.2),
              alpha= 0.5)+
  scale_y_continuous(limits = c(-1,6))+
  facet_wrap(~month)
```

## H

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_fn1,
                  ymax = H.c_fn1 + H.c_fn2,
                  ymin = H.c_fn1 - H.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```

## LE

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_fn1,
                  ymax = LE.c_fn1 + LE.c_fn2,
                  ymin = LE.c_fn1 - LE.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```


## Net Rad

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,RN_6_5_1_1_1.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = RN_6_5_1_1_1.c_fn1,
                  ymax = RN_6_5_1_1_1.c_fn1 + RN_6_5_1_1_1.c_fn2,
                  ymin = RN_6_5_1_1_1.c_fn1 - RN_6_5_1_1_1.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
levels(diel$month)
```


# Save

```{r, warning=FALSE}
df <- df[!duplicated(df$TIMESTAMP), ]

write.csv(x = df,file = 'C:/Users/dtrangmoe/Documents/sites/churchill/data/Churchill_Met_Flux_Clean_Ameriflux_2025.csv',row.names = F,quote = F)
```

