---
title: "Churchill Cleaning"
output:
  html_document:
    df_print: paged
date: "2022-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/github/churchill_cleaning_processing') #use this to set your directory
```



# Load 

```{r, warning=FALSE}
rm(list = ls())
Sys.setenv(TZ = "UTC")

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(lubridate)
Sys.setenv(TZ = "UTC")
```


Read in uncleaned file
```{r}

df <- fread('./outputs/cleaning/Churchill_met_flux_merged_aligned_2025.csv')

```

Plots every biomet variable, looks for issues and cleans when necessary

Some variables add a ".c" at the end even if no cleaning is done because this
makes it easier for future filed to merge with past files!

# Air T 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,TA_2_1_1_1_1),col='black')+
  scale_y_continuous(#limits = c(-40,40),
                     expression('Air Temperature ('*Celsius*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-03-01', '2026-01-01')))

df$TA_2_1_1_1_1.c <- df$TA_2_1_1_1_1

```

#Relative Humidity 

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_19_3_1_1_1),col='black')+
  scale_y_continuous(#limits = c(20,100),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))

```

Remove problematic chunk at beginning of dataset
```{r}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_19_3_1_1_1),col='black')+
  scale_y_continuous(#limits = c(20,100),
                     expression('Relative Humidity ('*percent*')'))+
  geom_vline(xintercept = as.POSIXct("2022-09-22"))+
  scale_x_datetime(limits = as.POSIXct(c("2022-08-01","2022-12-31")))

RH_19_3_1_1_1.limits <- ifelse(df$TIMESTAMP < as.POSIXct('2022-09-22'),NA,df$RH_19_3_1_1_1)

df$RH_19_3_1_1_1.c <- RH_19_3_1_1_1.limits

plot(df$RH_19_3_1_1_1.c)
```


# Barometric Pressure 

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1),col='black')+
  scale_y_continuous(limits = c(0,120),
                     expression ('Barometric Pressure ('*kPa*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))
```

Unit adjustment and cleaning
```{r}

PA_4_2_1_1_1.limits <- df$PA_4_2_1_1_1

# Adjust units in Pa to kPa
PA_4_2_1_1_1.limits <- ifelse(PA_4_2_1_1_1.limits > 150, PA_4_2_1_1_1.limits/1000 ,PA_4_2_1_1_1.limits)

# Correct incorrect unit adjustment
PA_4_2_1_1_1.limits <- ifelse(PA_4_2_1_1_1.limits < 10, PA_4_2_1_1_1.limits*100 ,PA_4_2_1_1_1.limits)

plot(PA_4_2_1_1_1.limits)
summary(PA_4_2_1_1_1.limits)

# Remove outside of absolute limits - picked 97 due to problematic chunk in 2022
PA_4_2_1_1_1.limits <- ifelse(PA_4_2_1_1_1.limits < 97 | PA_4_2_1_1_1.limits > 110, NA ,PA_4_2_1_1_1.limits)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PA_4_2_1_1_1.limits),col='black')+
  scale_y_continuous(#limits = c(0,200),
                     expression ('Barometric Pressure ('*kPa*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))+
  scale_y_continuous(limits = c(90, 115))

df$PA_4_2_1_1_1.c <- PA_4_2_1_1_1.limits



```


#Soil Heat Flux 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SHF_6_37_1_1_1,col='SHF 1'))+
  geom_point(aes(TIMESTAMP,SHF_6_37_2_1_1,col='SHF 2'))+
  scale_y_continuous(limits = c(-80,190),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','black'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))

df$SHF_6_37_1_1_1.c <- df$SHF_6_37_1_1_1
df$SHF_6_37_2_1_1.c <- df$SHF_6_37_2_1_1
```

# Snow Depth 

Turns snow-free season into NAs - dates picked manually
```{r, warning=FALSE}
hist(df$SD_10_99_1_1_1,breaks=100)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1),col='black')+
  #geom_line(aes(TIMESTAMP,PPFDR_7_23_1_1_1/500), col = 'green')+
  scale_y_continuous(limits = c(-.5,5),
                     expression('Snow Depth ('*m*')'))+
  geom_hline(yintercept = 0, color = "red")+
  geom_hline(yintercept = 1, color = "red")+
  geom_vline(xintercept = as.POSIXct("2025-05-23"), color = "red")+ # Y3 Spring
  geom_vline(xintercept = as.POSIXct("2025-10-26"), color = "red")+ # Y3 Fall
  geom_vline(xintercept = as.POSIXct("2024-5-19"), color = "red")+ # Y2 Spring
  geom_vline(xintercept = as.POSIXct("2024-10-25"), color = "red")+ # Y2 Fall
  geom_vline(xintercept = as.POSIXct("2023-5-18"), color = "red")+ # Y1 Spring
  geom_vline(xintercept = as.POSIXct("2023-10-26"), color = "red")+ # Y1 Fall
  geom_vline(xintercept = as.POSIXct("2022-10-16"), color = "red") # Y0 Fall


SD_10_99_1_1_1.limits=df$SD_10_99_1_1_1
SD_10_99_1_1_1.limits = ifelse(df$SD_10_99_1_1_1 < 0,0,SD_10_99_1_1_1.limits)
SD_10_99_1_1_1.limits = ifelse(df$SD_10_99_1_1_1 > 1,NA,SD_10_99_1_1_1.limits)

# Remove 2025 growing season
SD_10_99_1_1_1.limits = ifelse(df$TIMESTAMP > as.POSIXct('2025-05-23') & df$TIMESTAMP < as.POSIXct('2025-10-26'),NA,SD_10_99_1_1_1.limits)

# Remove 2024 growing season
SD_10_99_1_1_1.limits = ifelse(df$TIMESTAMP > as.POSIXct('2024-05-19') & df$TIMESTAMP < as.POSIXct('2024-10-25'),NA,SD_10_99_1_1_1.limits)

# Remove 2023 growing season
SD_10_99_1_1_1.limits = ifelse(df$TIMESTAMP > as.POSIXct('2023-05-18') & df$TIMESTAMP < as.POSIXct('2023-10-26'),NA,SD_10_99_1_1_1.limits)

# Remove 2022 growing season
SD_10_99_1_1_1.limits = ifelse(df$TIMESTAMP < as.POSIXct('2022-10-16'),NA,SD_10_99_1_1_1.limits)
                               
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits),col='black')+
  scale_y_continuous(#limits = c(-.25,.75),
                     expression('Snow Depth ('*m*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))

```

## Rolling MAD
```{r, warning=FALSE}
f = SD_10_99_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

```

```{r, warning=FALSE}

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits,col='Snow Depth'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-.1,.8))+
  scale_x_datetime(limits = as.POSIXct(c('2025-08-01', '2026-01-01'),format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 2

#Add clean value to dataframe (_.c)

df$SD_10_99_1_1_1.c = ifelse(abs(SD_10_99_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SD_10_99_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-0.75,1))+
  scale_x_datetime(limits = as.POSIXct(c('2025-08-01', '2026-01-01'),format="%F"))+
  scale_color_manual(values=c('black','red'))
```


```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SD_10_99_1_1_1.c),col='black')+
  geom_line(aes(TIMESTAMP,WS_16_33_1_1_1/10),col='black')+
  #scale_y_continuous(limits = c(-.25,.5))+
  scale_x_datetime(limits = as.POSIXct(c('2025-10-06','2025-12-30'),format="%F"))

```


# PAR 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFD_7_21_1_1_1),col='black')+
  scale_x_datetime(limits = as.POSIXct(c("2022-07-01","2026-01-01")))+
  scale_y_continuous(#limits = c(-25,2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))


#make sure max and min make sense here - no negatives!!
summary(df$PPFD_7_21_1_1_1)
```

```{r, warning=FALSE}

## Use this chunk to remove out liars if needed
# hist(df$PPFD_7_21_1_1_1,breaks=100)
# plot(df$TIMESTAMP,df$PPFD_7_21_1_1_1,ylim = c(0,1850));abline(h=1750, col= 'red');abline(h=0, col='red')
# PPFD_7_21_1_1_1.limits = replace(df$PPFD_7_21_1_1_1, df$PPFD_7_21_1_1_1 < 0 | df$PPFD_7_21_1_1_1 > 1750,NA)
# hist(PPFD_7_21_1_1_1.limits,breaks=100)
# plot(PPFD_7_21_1_1_1.limits)

df$PPFD_7_21_1_1_1.c <- df$PPFD_7_21_1_1_1
```

# PAR Reflected 

There are some off points here but I tried a rolling filter with no luck - could add very specific absolute limits if needed
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFDR_7_23_1_1_1),col='black')+
  scale_x_datetime(limits = as.POSIXct(c("2022-07-01","2026-01-01")))+
  scale_y_continuous(#limits = c(-25,1600),
                     expression('PAR Reflected ('*mu*mol/m^2/s*')'))+
  geom_hline(yintercept = 800)

## Remove weird 2022 chunk

PPFDR_7_23_1_1_1.limits <- ifelse(year(df$TIMESTAMP) == 2022 & df$PPFDR_7_23_1_1_1 > 800, NA, df$PPFDR_7_23_1_1_1)

#make sure max/min make sense here - no negatives!!
summary(PPFDR_7_23_1_1_1.limits)

df$PPFDR_7_23_1_1_1.c <- PPFDR_7_23_1_1_1.limits
```

# Net Radiation 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, RN_6_5_1_1_1),col='black')+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))+
  scale_y_continuous(#limits = c(-125,850),
                     expression('Net Radiation ('*W/m^2*')'))

summary(df$RN_6_5_1_1_1)
```

```{r, warning=FALSE}
RN_6_5_1_1_1.limits <- df$RN_6_5_1_1_1
hist(df$RN_6_5_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$RN_6_5_1_1_1,ylim = c(-400,850));abline(h=780,col= 'red');abline(h=-150, col='red')
RN_6_5_1_1_1.limits = replace(df$RN_6_5_1_1_1, df$RN_6_5_1_1_1 < -150 | df$RN_6_5_1_1_1 > 780,NA)
hist(RN_6_5_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,RN_6_5_1_1_1.limits)


df$RN_6_5_1_1_1.c <- RN_6_5_1_1_1.limits
```

# Shortwave in 

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWIN_6_10_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))+
  scale_y_continuous(#limits = c(-10,1000),
                     expression('Shortwave In ('*W/m^2*')'))

#check for funky values - no negatives!
summary(df$SWIN_6_10_1_1_1)
```


```{r, warning=FALSE}

#Get rid of negatives
SWIN_6_10_1_1_1.limits <- df$SWIN_6_10_1_1_1

SWIN_6_10_1_1_1.limits[df$SWIN_6_10_1_1_1 < 0] <- 0

df$SWIN_6_10_1_1_1.c <- SWIN_6_10_1_1_1.limits

```


# Shortwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWOUT_6_11_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))+
  scale_y_continuous(limits = c(-10,750),
                     expression('Shortwave Out ('*W/m^2*')'))

#Check for funky values - no negatives!
summary(df$SWOUT_6_11_1_1_1)
```


```{r, warning=FALSE}
# Get rid of negatives
SWOUT_6_11_1_1_1.limits <- df$SWOUT_6_11_1_1_1

SWOUT_6_11_1_1_1.limits[df$SWOUT_6_11_1_1_1 < 0] <- 0

df$SWOUT_6_11_1_1_1.c <- SWOUT_6_11_1_1_1.limits
```


# Albedo 
```{r, warning=FALSE}
albedo = df$SWOUT_6_11_1_1_1.c / df$SWIN_6_10_1_1_1.c

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo))+
  scale_y_continuous(limits = c(-0.2,5),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))

albedo.limits = replace(albedo, albedo < .05 | albedo > 1,NA)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo.limits))+
  scale_y_continuous(limits = c(-.2,1.2),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))


```

## Rolling MAD
```{r, warning=FALSE}
f = albedo.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Albedo'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,1))+
  scale_x_datetime(limits = as.POSIXct(c('2025-08-01', '2026-01-01'),format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 2

#Add clean value to dataframe (_.c)

df$ALB_1_1_1.c = ifelse(abs(albedo.limits - mad_filt) > (N * roll.mad),NA,albedo.limits)

#Compare cleaned vs. uncleaned


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$ALB_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,1))+
  scale_color_manual(values=c('black','red'))


```

# Longwave In 
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWIN_6_14_1_1_1))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))+
  scale_y_continuous(#limits = c(50,750),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))


hist(df$LWIN_6_14_1_1_1,breaks=100)

```

```{r, warning=FALSE}

#Get rid of weird 2022 chunk
LWIN_6_14_1_1_1.limits = replace(df$LWIN_6_14_1_1_1, df$LWIN_6_14_1_1_1 > 500,NA)

df$LWIN_6_14_1_1_1.c = LWIN_6_14_1_1_1.limits

hist(df$LWIN_6_14_1_1_1.c)

```


# Longwave out 
```{r, warning=FALSE}

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWOUT_6_15_1_1_1))+
  scale_y_continuous(#limits = c(150,750),
                     expression('Longwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))

hist(df$LWOUT_6_15_1_1_1,breaks=100)

```

```{r, warning=FALSE}

LWOUT_6_15_1_1_1.limits = replace(df$LWOUT_6_15_1_1_1, df$LWOUT_6_15_1_1_1 > 550,NA)

df$LWOUT_6_15_1_1_1.c = LWOUT_6_15_1_1_1.limits

hist(df$LWOUT_6_15_1_1_1.c)

```

# Water Temp (From water table depth sensor)

```{r}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,TW_2_45_1_1_1))+
  scale_y_continuous(#limits = c(150,750),
                     expression('Water Temp (Celcius)'))+
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01","2025-11-30")))+
  geom_vline(aes(xintercept = as.POSIXct('2025-05-25')))+
  geom_vline(aes(xintercept = as.POSIXct('2025-11-05'))) #ref. for cutting freezing water table depth data

```

# Water Table Depth

```{r}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,WTD_10_42_1_1_1))+
  scale_y_continuous(#limits = c(150,750),
                     expression('Water Table Depth (m)'))+
  scale_x_datetime(limits = as.POSIXct(c(c('2025-06-01', '2026-01-01'))))+
  geom_vline(aes(xintercept = as.POSIXct('2025-05-25')))+
  geom_vline(aes(xintercept = as.POSIXct('2025-11-05')))  #for cutting freezing water table depth data


df$WTD_10_42_1_1_1.c <- ifelse(df$TIMESTAMP < as.POSIXct('2025-05-25') | df$TIMESTAMP > as.POSIXct('2025-11-05'), NA, df$WTD_10_42_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,WTD_10_42_1_1_1.c))+
  scale_y_continuous(#limits = c(150,750),
                     expression('Water Table Depth (m)'))+
  scale_x_datetime(limits = as.POSIXct(c(c('2022-08-01', '2026-01-01'))))


```



# Soil Temps

## CS655 Temps
```{r}

ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_1_1_1,color='1_1'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_1_1,color='2_1'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_2_1,color='2_2'))


## Convert these to kelvin separately

TS_2_38_1_1_1.limits <- ifelse(df$TS_2_38_1_1_1 > 200, df$TS_2_38_1_1_1 - 273.15, df$TS_2_38_1_1_1)
TS_2_38_2_1_1.limits <- ifelse(df$TS_2_38_2_1_1 > 200, df$TS_2_38_2_1_1 - 273.15, df$TS_2_38_2_1_1)
TS_2_38_2_2_1.limits <- ifelse(df$TS_2_38_2_2_1 > 200, df$TS_2_38_2_2_1 - 273.15, df$TS_2_38_2_2_1)

df$TS_2_38_1_1_1.c <- TS_2_38_1_1_1.limits
df$TS_2_38_2_1_1.c <- TS_2_38_2_1_1.limits
df$TS_2_38_2_2_1.c <- TS_2_38_2_2_1.limits

ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_1_1_1.c,color='1_1'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_1_1.c,color='2_1'))+
  geom_line(aes(TIMESTAMP,TS_2_38_2_2_1.c,color='2_2'))


```

##All Hummock Therms
```{r}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_4_1_1,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_2_1,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_3_1,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_4_1,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_4_5_1,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_6_1,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_7_1,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_8_1,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_9_1,color='70 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_10_1,color='80 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_11_1,color='90 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_12_1,color='1 m'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))
```
  

## All Open Water therms
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_3_1_1,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_2_1,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_3_1,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_4_1,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_3_5_1,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_6_1,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_7_1,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_8_1,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_9_1,color='70 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_10_1,color='80 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_11_1,color='90 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_12_1,color='1 m'))+
  scale_x_datetime(limits = as.POSIXct(c('2022-08-01', '2026-01-01')))
```

Bulk temp cleaning
Does kelvin conversion, removes problematic chunk
```{r}

# time window to remove
start_time <- as.POSIXct("2022-10-21", tz = "UTC")
end_time   <- as.POSIXct("2022-11-07", tz = "UTC")

# TS variables to process
ts_vars <- c(
  paste0("TS_2_38_4_", 1:12, "_1"),
  paste0("TS_2_38_3_", 1:12, "_1")
)

# logical index for rows to remove
time_idx <- df$TIMESTAMP >= start_time & df$TIMESTAMP <= end_time

# loop
for (v in ts_vars) {

  # Kelvin → Celsius conversion
  x <- ifelse(df[[v]] > 200, df[[v]] - 273.15, df[[v]])
  
  # Absolute limits removal
  x <- ifelse(df[[v]] > 40 | df[[v]] < -40, NA, df[[v]])

  # remove time chunk
  x[time_idx] <- NA

  # save as standalone .limits object
  assign(paste0(v, ".limits"), x)
}

```

Random 2022 problematic chunks
```{r}

#3_1_1
plot(TS_2_38_3_1_1.limits)
TS_2_38_3_1_1.limits[0:5400] <- NA
TS_2_38_3_1_1.limits[11700:15300] <- NA
plot(TS_2_38_3_1_1.limits)

#3_12_1
plot(TS_2_38_3_12_1.limits)
TS_2_38_3_12_1.limits[0:15500] <- NA
plot(TS_2_38_3_12_1.limits)

#4_11_1
plot(TS_2_38_4_11_1.limits)
TS_2_38_4_11_1.limits[0:9600] <- NA
TS_2_38_4_11_1.limits[13000:15300] <- NA
plot(TS_2_38_4_11_1.limits)

#4_12_1
plot(TS_2_38_4_12_1.limits)
TS_2_38_4_12_1.limits[15200:18000] <- NA
plot(TS_2_38_4_12_1.limits)

```


```{r}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_4_1_1.limits,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_2_1.limits,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_3_1.limits,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_4_1.limits,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_4_5_1.limits,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_6_1.limits,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_7_1.limits,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_8_1.limits,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_9_1.limits,color='70 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_10_1.limits,color='80 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_11_1.limits,color='90 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_4_12_1.limits,color='1 m'))+
  scale_x_datetime(limits = as.POSIXct(c("2022-07-01","2026-01-01")))
```
  

```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_2_38_3_1_1.limits,color='Surface'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_2_1.limits,color='5 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_3_1.limits,color='10 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_4_1.limits,color='20 cm'))+  
  geom_line(aes(TIMESTAMP,TS_2_38_3_5_1.limits,color='30 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_6_1.limits,color='40 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_7_1.limits,color='50 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_8_1.limits,color='60 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_9_1.limits,color='70 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_10_1.limits,color='80 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_11_1.limits,color='90 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_38_3_12_1.limits,color='1 m'))+
  scale_x_datetime(limits = as.POSIXct(c("2022-07-01","2026-01-01")))
```

## Hummocks clean

```{r, warning=FALSE}

df$TS_2_38_4_1_1.c <- TS_2_38_4_1_1.limits
df$TS_2_38_4_2_1.c <- TS_2_38_4_2_1.limits
df$TS_2_38_4_3_1.c <- TS_2_38_4_3_1.limits
df$TS_2_38_4_4_1.c <- TS_2_38_4_4_1.limits
df$TS_2_38_4_5_1.c <- TS_2_38_4_5_1.limits
df$TS_2_38_4_6_1.c <- TS_2_38_4_6_1.limits
df$TS_2_38_4_7_1.c <- TS_2_38_4_7_1.limits
df$TS_2_38_4_8_1.c <- TS_2_38_4_8_1.limits
df$TS_2_38_4_9_1.c <- TS_2_38_4_9_1.limits
df$TS_2_38_4_10_1.c <- TS_2_38_4_10_1.limits
df$TS_2_38_4_11_1.c <- TS_2_38_4_11_1.limits
df$TS_2_38_4_12_1.c <- TS_2_38_4_12_1.limits

```

## Open Water clean

```{r, warning=FALSE}

df$TS_2_38_3_1_1.c <- TS_2_38_3_1_1.limits
df$TS_2_38_3_2_1.c <- TS_2_38_3_2_1.limits
df$TS_2_38_3_3_1.c <- TS_2_38_3_3_1.limits
df$TS_2_38_3_4_1.c <- TS_2_38_3_4_1.limits
df$TS_2_38_3_5_1.c <- TS_2_38_3_5_1.limits
df$TS_2_38_3_6_1.c <- TS_2_38_3_6_1.limits
df$TS_2_38_3_7_1.c <- TS_2_38_3_7_1.limits
df$TS_2_38_3_8_1.c <- TS_2_38_3_8_1.limits
df$TS_2_38_3_9_1.c <- TS_2_38_3_9_1.limits
df$TS_2_38_3_10_1.c <- TS_2_38_3_10_1.limits
df$TS_2_38_3_11_1.c <- TS_2_38_3_11_1.limits
df$TS_2_38_3_12_1.c <- TS_2_38_3_12_1.limits

```


# Save

```{r, warning=FALSE}
write.csv(x = df,file = './outputs/cleaning/Churchill_merged_met_clean_2025.csv',row.names = F,quote = F)
```

