---
title: "Data Quality Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/github/churchill_cleaning_processing') #use this to set your directory
```


This file generates plots for the monthly data check meetings. It doesn't do
any cleaning or processing- not necessary to run this to get cleaned data set

# Load packages, cleaned data 
```{r, include=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
```


```{r, include = FALSE}

df <- fread('./data/cleaned/Churchill_Met_Flux_Clean_Ameriflux_2025.csv')

df$ts <- df$ts-6*3600 #adjust timezone from UTC to CST
df$TIMESTAMP <- df$TIMESTAMP-6*3600 #adjust timezone from UTC to CST

df_month <- subset(df, df$TIMESTAMP >= as.POSIXct("2025-09-01 0000", tz = "UTC"))


# data formatting for flag plots

df$co2_flux.flag <- as.factor(df$co2_flux.flag)
df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```



# Timeseries Plots

## Year-to-Date CO2
```{r}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
  scale_x_datetime(limits = as.POSIXct(c("2025-01-01", "2025-09-20")))+
  labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
scale_color_manual(values = color_map, name = "Cleaning Flag")
nee_plot_ytd
```


## Previous Month CO2
```{r}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-09-01", "2025-09-30")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_month

```


## Week zoom-in CO2
```{r}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-09-08", "2025-09-15")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_week

```



## Year-to-Date Methane
```{r}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_year = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.33))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-01-01", "2025-09-30")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_year

```


## Previous Month Methane
```{r}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.33))+  
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-09-01", "2025-09-30")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_month

```


## Week zoom-in Methane
```{r}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.33))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-09-08", "2025-09-15")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_week

```



# Energy Balance Plots

## Full Year-to-date
```{r}

df$met = ((df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c) -
         (df$LWOUT_6_15_1_1_1.c + df$SWOUT_6_11_1_1_1.c)) -
        ((df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2)
df$flux = df$H.c + df$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)


# Plot
eb_ytd <- ggplot(df, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Full Year EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_ytd
```


## Previous Month
```{r}

df_month$met = ((df_month$LWIN_6_14_1_1_1.c + df_month$SWIN_6_10_1_1_1.c) -
         (df_month$LWOUT_6_15_1_1_1.c + df_month$SWOUT_6_11_1_1_1.c)) -
        ((df_month$SHF_6_37_1_1_1.c + df_month$SHF_6_37_2_1_1.c)/2)
df_month$flux = df_month$H.c + df_month$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df_month)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)

# Plot
eb_month <- ggplot(df_month, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Previous Month EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_month

```



# Timestamp Alignment Check

Create potential radiation dataset
```{r}
ts <- as.POSIXct(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                           to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                           by = 60*30),'yyyy-mm-dd HH:MM:SS', tz = 'UTC')

JD <- as.numeric(format(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                           to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                           by = 60*30),'%j'))
h <- as.numeric(format(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                           to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                           by = 60*30),'%H'))
m <- as.numeric(format(seq(from = as.POSIXct('2025-01-01 00:00', tz = 'UTC'),
                          to = as.POSIXct('2025-10-01 00:00', tz = 'UTC'),
                          by = 60*30),'%M'))
H <- h+ifelse(m == 30,0.5,0)

rpot <- potential.radiation(doy = JD,hour = H,latDeg = 59,longDeg = -94,timezone = -6,useSolartime = F)

rpot <- as.data.frame(cbind(ts, rpot))

df <- merge(df, rpot, by = 'ts', all.x = T)

#check that it worked
ggplot(data = df)+
  geom_line(aes(x = ts, y = rpot), color = "blue2")+
  geom_line(aes(x = ts, y = SWIN_6_10_1_1_1.c))+
  scale_x_datetime(limits = as.POSIXct(c("2025-03-01", "2025-03-10")))
  #geom_vline(xintercept = as.POSIXct("2025-07-03 7:00"))

ggplot(data = df)+
  geom_point(aes(x = rpot, y = SWIN_6_10_1_1_1.c))

```

## Full Year-to-Date
```{r}


```


## Previous Month
```{r}


```


## Four-panel full timeseries check for entire month
```{r}


```



# Diurnal Fluxes

set hour and month vectors to be able to take the averages

```{r, warning=FALSE}
df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c,hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

## NEE

```{r, warning=FALSE}
diurnal_nee <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_nee
```

## CH4

```{r, warning=FALSE}
diurnal_ch4 <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_ch4

```

