---
title: "3_churchill_flux_cleaning"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/github/churchill_cleaning_processing') #use this to set your directory
```


# Flux Cleaning

```{r, warning=FALSE}
rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork)
Sys.setenv(TZ = "UTC")
```

Load in cleaned met data and flux data

```{r warning=FALSE}

df <- fread('./outputs/cleaning/Churchill_merged_met_clean_2025.csv')

```


Creates a variable to input a date range for the plots in the flux section of
cleaning code. Used to easily change date range for different data sets. 
```{r, warning=FALSE}
flux_dates <- c('2025-01-01', '2025-11-30')
```

## Create Flags

```{r, warning=FALSE}
df$Tau.flag <- as.numeric(df$qc_Tau)
df$co2_flux.flag <- as.numeric(df$qc_co2_flux)
df$ch4_flux.flag <- as.numeric(df$qc_ch4_flux)
df$LE.flag <- as.numeric(df$qc_LE)
df$H.flag <- as.numeric(df$qc_H)


#check that it worked
plot(df$qc_co2_flux, df$co2_flux.flag)

```

# Designate winter vs. summer

```{r}
# 
# # Use daily average 5cm soil temperature to determine winter vs. summer cleaning regions
# 
# df_daily <- df %>%
#   mutate(date = as.Date(TIMESTAMP),
#          year = year(TIMESTAMP)) %>%
#   group_by(year, date) %>%
#   summarise(
#     soil_temp = mean(TS_2_38_3_2_1.c, na.rm = TRUE),
#     .groups = "drop"
#   ) %>%
#   mutate(season_year = if_else(month(date) >= 7, year + 1L, year))
# 
# find_transition_date <- function(dates, temps, threshold = 0, n_days = 3, direction = "thaw") {
#   
#   if (direction == "thaw") {
#     condition <- temps > threshold
#   } else {
#     condition <- temps < threshold
#   }
#   
#   rle_cond <- rle(condition)
#   idx <- which(rle_cond$values & rle_cond$lengths >= n_days)[1]
#   
#   if (is.na(idx)) return(NA)
#   
#   start_pos <- sum(rle_cond$lengths[seq_len(idx - 1)]) + 1
#   dates[start_pos]
# }
# 
# summer_start <- df_daily %>%
#   group_by(year) %>%
#   summarise(
#     summer_start = find_transition_date(date, soil_temp, direction = "thaw"),
#     .groups = "drop"
#   ) %>%
#   rename(season_year = year)
# 
# winter_start <- df_daily %>%
#   group_by(year) %>%
#   summarise(
#     winter_start = find_transition_date(date, soil_temp, direction = "freeze"),
#     .groups = "drop"
#   ) %>%
#     rename(season_year = year)

# Manually assign seasonal definitions

df <- df %>%
  mutate(
      season = case_when(
      (TIMESTAMP <= as.POSIXct("2022-10-16 0000")) ~ 'summer',
      
      (TIMESTAMP > as.POSIXct("2022-10-16 0000") & TIMESTAMP <= as.POSIXct("2023-05-04 0000")) ~ 'winter',
      
      (TIMESTAMP > as.POSIXct("2023-05-04 0000") & TIMESTAMP <= as.POSIXct("2023-10-21 0000")) ~ 'summer',
      
      (TIMESTAMP > as.POSIXct("2023-10-21 0000") & TIMESTAMP <= as.POSIXct("2024-05-14 0000")) ~ 'winter',
      
      (TIMESTAMP > as.POSIXct("2024-05-14 0000") & TIMESTAMP <= as.POSIXct("2024-10-19 0000")) ~ 'summer',
      
      (TIMESTAMP > as.POSIXct("2024-10-19 0000") & TIMESTAMP <= as.POSIXct("2025-05-21 0000")) ~ 'winter',
      
      (TIMESTAMP > as.POSIXct("2025-05-21 0000") & TIMESTAMP <= as.POSIXct("2025-10-20 0000")) ~ 'summer',

      (TIMESTAMP > as.POSIXct("2025-10-20 0000")) ~ 'winter',
      TRUE ~ NA_character_
    )
  )


summary(df$season)

ggplot(data = df)+
  geom_point(aes(x = TIMESTAMP, y = co2_flux, color = season))
```


# Initial Clean

## EP QC

filter by the eddypro flags and create new variable _.qc

```{r, warning=FALSE}
Tau.qc      = replace(df$Tau,df$qc_Tau == 2,NA)
co2_flux.qc = replace(df$co2_flux,df$qc_co2_flux == 2,NA)
ch4_flux.qc = replace(df$ch4_flux,df$qc_ch4_flux == 2,NA)
LE.qc       = replace(df$LE,df$qc_LE == 2,NA)
H.qc        = replace(df$H,df$qc_H == 2,NA)
```

## Diagnostics cleaning
Clean some data based on instrument diagnostics
```{r}
signal.threshold.co2 = ifelse(df$co2_signal_strength_7200_mean >= 75,0,1)
signal.threshold.h2o = ifelse(df$h2o_signal_strength_7200_mean >= 75,0,1)
signal.threshold.ch4 = ifelse(df$rssi_77_mean >= 10,0,1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,co2_flux,color=signal.threshold.co2))+
  scale_y_continuous(limits = c(-20,20))

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,ch4_flux,color=signal.threshold.ch4))+
  scale_y_continuous(limits = c(-0.5,0.25))

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LE,color=signal.threshold.h2o))+
  scale_y_continuous(limits = c(-200,500))


co2_flux.ss = replace(df$co2_flux, df$co2_signal_strength_7200_mean <= 75,NA)
ch4_flux.ss = replace(df$ch4_flux, df$rssi_77_mean <= 10,NA)
LE.ss       = replace(df$LE, df$h2o_signal_strength_7200_mean <= 75,NA)

# Make .flag = 5 everywhere where cleaning is done via signal strength
df$co2_flux.flag <- ifelse(is.na(co2_flux.ss) & !is.na(df$co2_flux) & df$co2_flux.flag != 2, 5, df$co2_flux.flag)

# Make .flag = 5 everywhere where cleaning is done via signal strength
df$ch4_flux.flag <- ifelse(is.na(ch4_flux.ss) & !is.na(df$ch4_flux) & df$ch4_flux.flag != 2, 5, df$ch4_flux.flag)

# Make .flag = 5 everywhere where cleaning is done via signal strength
df$LE.flag <- ifelse(is.na(LE.ss) & !is.na(df$LE) & df$LE.flag != 2, 5, df$LE.flag)

```


## Clear Outliers

look for absolute outliers and manually set some absolute limits to remove crazy data

### Tau

Plot Tau Histogram

```{r, warning=FALSE}
hist(df$Tau,breaks=100)
```

Cut the crazy data and create new variable (Tau.limits)

```{r, warning=FALSE}

Tau.limits = df$Tau
Tau.limits = replace(Tau.limits, df$Tau < -0.8 | df$Tau > .1,NA)

# Make .flag = 3 everywhere where cleaning is done via absolute limits
df$Tau.flag <- ifelse(is.na(Tau.limits) & !is.na(df$Tau) & df$Tau.flag != 2, 3, df$Tau.flag)

hist(Tau.limits, breaks = 100)
```

### NEE

Plot NEE and what we might clean

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(x = TIMESTAMP, y = co2_flux))+
  geom_hline(yintercept = c(-15,12))

#This filter removes points outside of absolute limits and high uptake, low light points
co2_flux.limits <- df$co2_flux
co2_flux.limits = replace(co2_flux.limits, (df$co2_flux > 12 | df$co2_flux < -15 | (df$co2_flux < -5 & df$PPFD_7_21_1_1_1.c < 150)),NA)


# Make .flag = 3 everywhere where cleaning is done via absolute limits
df$co2_flux.flag <- ifelse(is.na(co2_flux.limits) & !is.na(df$co2_flux) & df$co2_flux.flag != 2 & df$co2_flux.flag != 5, 3, df$co2_flux.flag)

```



### CH4

Plot CH4 and what we might clean

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,ch4_flux))+
  scale_y_continuous(limits = c(-1,1))+
  geom_hline(yintercept = c(-0.2,0.4))

ch4_flux.limits <- df$ch4_flux
ch4_flux.limits = replace(ch4_flux.limits, (df$ch4_flux < -0.2 | df$ch4_flux > 0.4),NA)

# Make .flag = 3 everywhere where cleaning is done via absolute limits
df$ch4_flux.flag <- ifelse(is.na(ch4_flux.limits) & !is.na(df$ch4_flux) & df$ch4_flux.flag != 2 & df$ch4_flux.flag != 5, 3, df$ch4_flux.flag)
```


### H

Plot H and what we might clean

Clean based on graphs, create new variable (H.limits), and see cleaned product

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,H))+
  scale_y_continuous(limits = c(-200,500))+
  geom_hline(yintercept = c(-200,350)) ## expand absolute limits here to do less cleaning

H.limits <- df$H
H.limits=replace(H.limits, df$H < -200 | df$H > 350, NA)

# Make .flag = 3 everywhere where cleaning is done via absolute limits
df$H.flag <- ifelse(is.na(H.limits) & !is.na(df$H) & df$H.flag != 2, 3, df$H.flag)
```

### LE

Plot LE Histogram and what we might clean

Clean based on graphs, create new variable (H.limits), and see cleaned product

```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LE))+
  scale_y_continuous(limits = c(-200,500))+
  geom_hline(yintercept = c(-50,450))

LE.limits <- df$LE
LE.limits =replace(LE.limits, df$LE < -50 | df$LE > 450,NA)


# Make .flag = 3 everywhere where cleaning is done via absolute limits
df$LE.flag <- ifelse(is.na(LE.limits) & !is.na(df$LE) & df$LE.flag != 2 & df$LE.flag != 5, 3, df$LE.flag)

```

## USTAR

use night-time only flux values and plot Ustar based on data drop off

```{r, warning=FALSE}
clean.co2 = ifelse(co2_flux.limits == 1 |
                   co2_flux.qc == 2 |
                   signal.threshold.co2 == 1,NA,df$co2_flux)

df$nightCO2 = clean.co2
df$nightCO2 = replace(df$nightCO2,df$SWIN_6_10_1_1_1 > 10,NA)

Uthreshold=0.06
ggplot(data = df,aes(`u*`,nightCO2))+
  ylab(expression(paste("Flux (g-C", ~CO[2], ~"m",""^"-2","d",""^"-1",")")))+
  geom_point()+xlab("U*")+
  scale_x_continuous(limits = c(0,1))+
  scale_y_continuous(limits = c(-10,10))+
  geom_vline(xintercept = Uthreshold,col='red')
```

pick threshold and filter based on plots above, I liked .06


created flag to indicate where u* values are below our threshold- makes cleaning with u* optional but easy when using cleaned data sets
```{r, warning=FALSE}
df$u_flag = ifelse(df$`u*` < Uthreshold,1,0)
```

## Combine Cleaning

investigate the previous limits and combine all to create a new variable (clean), plot to see difference

```{r, warning=FALSE}
co2fluxclean = ifelse(is.na(co2_flux.qc) | is.na(co2_flux.limits) | is.na(co2_flux.ss),NA,df$co2_flux)

ch4fluxclean = ifelse(is.na(ch4_flux.qc) | is.na(ch4_flux.limits) | is.na(ch4_flux.ss),NA,df$ch4_flux)

Hclean = ifelse(is.na(H.qc) | is.na(H.limits),NA,df$H)

LEclean = ifelse(is.na(LE.qc) | is.na(LE.limits) | is.na(LE.ss),NA,df$LE)

Tauclean = ifelse(is.na(Tau.qc) | is.na(Tau.limits),NA,df$Tau)

plot(df$TIMESTAMP,co2fluxclean)
plot(df$TIMESTAMP,ch4fluxclean)
plot(df$TIMESTAMP,Hclean)
plot(df$TIMESTAMP,LEclean)
plot(df$TIMESTAMP,Tauclean)
```

Add cleaned tau to dataframe (no MAD filter)
```{r, warning=FALSE}
df$Tau.c = Tauclean

df$Tau.flag <- as.factor(df$Tau.flag)
summary(df$Tau.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "pink3", "4" = "green4", "5" = "purple")

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

tau_plot = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Tau,color = Tau.flag))+
  geom_point(aes(TIMESTAMP,Tau.c),col='black')+
  #scale_y_continuous(limits=c(-12,8))+
  scale_x_datetime(limits = as.POSIXct(c('2025-01-01','2025-09-30')))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
tau_plot
```


# MAD Filter

Now, Spike filtering on half-hourly fluxes. For this type of data, filters based on median rather than std perform better. Use Unsymmetric Distributions and double MAD -MAD=Median Absolute Deviation for more info see link below <https://eurekastatistics.com/using-the-median-absolute-deviation-to-find-outliers/>

## NEE
```{r, warning=FALSE}
f = co2fluxclean # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2fluxclean,col='CO2 flux'))+
  geom_line(aes(TIMESTAMP,Flux_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-10,10))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```

now filter the data based on this signal

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm

## Use 3 here for 7200 summer, 7 for 7200 winter; in future use 4 for 7500
N.summer = 3
N.winter = 7
#Add clean value to dataframe (_.c)

df$co2_flux.c <- ifelse(
  df$season == "summer",
  ifelse(abs(co2fluxclean - Flux_filt) > (N.summer * roll.mad),NA,co2fluxclean),
    ifelse(abs(co2fluxclean - Flux_filt) > (N.winter * roll.mad),NA,co2fluxclean)
)


#Compare cleaned vs. uncleaned
ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux),col='red')+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-1,1))+
  scale_x_datetime(limits = as.POSIXct(c("2025-01-14","2025-02-20")))
```
See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,co2fluxclean),col='red')+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits = c(-40,40))+
  scale_x_datetime(limits = as.POSIXct(c('2025-09-15','2025-09-30'),format="%F"))+
  geom_line(aes(x = TIMESTAMP, y = PPFD_7_21_1_1_1.c/5000))
```

Add flag data
```{r}

df$co2_flux.flag <- ifelse(is.na(df$co2_flux.c) & !is.na(co2fluxclean) & df$co2_flux.flag != 2 & df$co2_flux.flag != 3 & df$co2_flux.flag != 5, 4, df$co2_flux.flag)

df$co2_flux.flag <- as.factor(df$co2_flux.flag)
summary(df$co2_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "pink3", "4" = "green4", "5" = "purple")

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,13))+
  scale_x_datetime(limits = as.POSIXct(c("2022-01-01", "2022-12-31")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot

```


## CH4
```{r, warning=FALSE}
 #apply the moving window filter
f = ch4fluxclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * 7 days (keep this at 7)
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4fluxclean,col='CH4 flux'))+
  geom_line(aes(TIMESTAMP,Flux_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-.25,.3))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```

adjust this (N) to tweak how many MADs to be away from the norm, CH4 deserves more because of it's nature, add clean value to the dataframe (_.c) and compare cleaned vs. uncleaned


```{r, warning=FALSE}
## Keep this consistent at 8

N = 8

df$ch4_flux.c = ifelse(abs(ch4fluxclean - Flux_filt) > (N * roll.mad),NA,ch4fluxclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,ch4_flux.c,col='cleaned'))+
  scale_y_continuous(limits = c(-.25,.3))+
  scale_x_datetime(limits = as.POSIXct(as.POSIXct(c('2025-03-04','2025-03-10'),format="%F"),format="%F"))+
  scale_color_manual(values=c('black','red'))
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
CH4Filter = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(df$TIMESTAMP,ch4fluxclean),col='red')+
  geom_point(aes(df$TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits = c(-.1,.5))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

CH4RSSI = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_line(aes(x=TIMESTAMP,y=rssi_77_mean))+
  scale_y_continuous(limits = c(-1,60))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

CH4RSSI = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_line(aes(x=TIMESTAMP,y=rssi_77_mean))+
  scale_y_continuous(limits = c(-1,60))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

#added co2 flux to compare co2/ch4 data coverage
CO2FLUX = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(x=TIMESTAMP,y=co2_flux))+
  scale_y_continuous(limits = c(-10,10))+
  scale_x_datetime(limits = as.POSIXct(c('2025-7-1','2025-9-1'),format="%F"))

CH4_FALLSOILTCOMP = plot_grid(CH4Filter,CH4RSSI,CO2FLUX,nrow=3,align = 'v')
CH4_FALLSOILTCOMP

```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,ch4fluxclean),col='red')+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits = c(-0.6,0.6))+
  scale_x_datetime(limits = as.POSIXct(c('2025-04-03','2025-08-10'),format="%F"))+
  geom_line(aes(x = TIMESTAMP, y = PPFD_7_21_1_1_1.c/100000))
```


Add flag data
```{r}

df$ch4_flux.flag <- ifelse(is.na(df$ch4_flux.c) & !is.na(ch4fluxclean) & df$ch4_flux.flag != 2 & df$ch4_flux.flag != 3, 4, df$ch4_flux.flag)

df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)
summary(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "pink3", "4" = "green4", "5" = "purple")

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.15,0.35))+
  scale_x_datetime(limits = as.POSIXct(c("2022-01-01", "2022-12-31")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot

```


## H
```{r, warning=FALSE}
# apply the moving window filter
f = Hclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Hclean,col='H'))+
  geom_line(aes(TIMESTAMP,Flux_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-180,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
```

Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm, add clean value to dataframe (_.c) and Compare Clean vs. Uncleaned

```{r, warning=FALSE}
#Leave at 3
N = 3

df$H.c = ifelse(abs(Hclean - Flux_filt) > (N * roll.mad),NA,Hclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,Hclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,H.c,col='cleaned'))+
  scale_y_continuous(limits=c(-150,350))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$TIMESTAMP,Hclean),col='red')+
  geom_point(aes(df$TIMESTAMP,H.c),col='black')+
  #scale_y_continuous(limits = c(-100,100))+
  scale_x_datetime(limits = as.POSIXct(c('2025-08-19','2025-09-24')))
```


Add flag data
```{r}

df$H.flag <- ifelse(is.na(df$H.c) & !is.na(co2fluxclean) & df$H.flag != 2 & df$H.flag != 3, 4, df$H.flag)

df$H.flag <- as.factor(df$H.flag)
summary(df$H.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "pink3", "4" = "green4", "5" = "purple")

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

h_plot = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,H,color = H.flag))+
  geom_point(aes(TIMESTAMP,H.c),col='black')+
  scale_y_continuous(limits=c(-300,600))+
  scale_x_datetime(limits = as.POSIXct(c("2022-01-01", "2022-12-31")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
h_plot
```

## LE

```{r, warning=FALSE}
# apply the moving window filter
f = LEclean # first make a new flux vector to apply the above filters

# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
Flux_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
Flux_filt = f                          # make a copy of the full fluxes again
Flux_filt[ind] = Flux_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = Flux_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(Flux_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LEclean,col='LE'))+
  geom_line(aes(TIMESTAMP,Flux_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-50,400))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('yellow','black','red'))
```

Now filter the data based on this signal (N) adjust this to tweak how many MADs to be away from the norm

```{r, warning=FALSE}
# Leave at 3
N = 3

df$LE.c = ifelse(abs(LEclean - Flux_filt) > (N * roll.mad),NA,LEclean)

ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LEclean,col='uncleaned'))+
  geom_point(aes(TIMESTAMP,LE.c,col='cleaned'))+
  scale_y_continuous(limits=c(-100,400))+
  scale_x_datetime(limits = as.POSIXct(flux_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

See data with multiple layers of the MAD filter to see if it should be changed

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*6,ymin = Flux_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*3,ymin = Flux_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*2,ymin = Flux_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = df$TIMESTAMP,ymax = Flux_filt+roll.mad*1,ymin = Flux_filt-roll.mad*1,fill='1'))+
  geom_point(aes(df$TIMESTAMP,LEclean),col='red')+
  geom_point(aes(df$TIMESTAMP,LE.c),col='black')+
  scale_y_continuous(limits = c(-20,20))+
  scale_x_datetime(limits = as.POSIXct(c('2025-01-20','2025-2-15')))
```


Add flag data
```{r}

df$LE.flag <- ifelse(is.na(df$LE.c) & !is.na(co2fluxclean) & df$LE.flag != 2 & df$LE.flag != 3, 4, df$LE.flag)

df$LE.flag <- as.factor(df$LE.flag)
summary(df$LE.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "pink3", "4" = "green4", "5" = "purple")

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

le_plot = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LE,color = LE.flag))+
  geom_point(aes(TIMESTAMP,LE.c),col='black')+
  #scale_y_continuous(limits=c(-12,8))+
  scale_x_datetime(limits = as.POSIXct(c("2022-01-01", "2022-12-31")))+
scale_color_manual(values = color_map, name = "QC LE")
le_plot

```


# Main Plots

```{r, warning=FALSE}
le <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,LE,col='Filt.'))+
  geom_point(aes(TIMESTAMP,LE.c,col='clean'))+
  scale_y_continuous(expression('LE ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))
  

h <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,H,col='Filt.'))+
  geom_point(aes(TIMESTAMP,H.c,col='clean'))+
  scale_y_continuous(expression('H ('*W~m^-2*')'))+
  scale_color_manual(values = c('black','red'))

co2 <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,col='Filt.'))+
  geom_point(aes(TIMESTAMP,co2_flux.c,col='clean'))+
  scale_y_continuous (expression('NEE ('*mu*mol~m^-2~s^-1*')'),
                      limits = c(-20,20))+
  scale_color_manual(values = c('black','red'))

ch4 <- ggplot(data = df)+theme_bw()+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux*43.2,col='Filt.'))+
  geom_point(aes(TIMESTAMP,ch4_flux.c*43.2,col='clean'))+
  scale_y_continuous(expression(CH[4]~'flux ('*mu*mol~m^-2~s^-1*')'),
                     limits = c(-3,8))+
  scale_color_manual(values = c('black','red'))



# png(filename = './png/mainplotsflux.png',width = 12,height = 8,units = 'in',res = 2000)
# co2 / ch4  + plot_layout(guides = "collect", axes = "collect")
# dev.off()
# 
# 
# png(filename = './png/mainplotseb.png',width = 12,height = 8,units = 'in',res = 2000)
# le / h  + plot_layout(guides = "collect", axes = "collect")
# dev.off()

```


## Energy Balance

combine energy fluxes by met and flux components

```{r}
df$met = (df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c) - (df$LWOUT_6_15_1_1_1.c + df$SWOUT_6_11_1_1_1.c)
df$flux = df$H.c + df$LE.c

plot(df$met, df$flux)

ggplot(data = df)+
  geom_point(aes(x = met, y = flux))+
  geom_abline(aes(slope = 1, intercept = 1))+
  scale_x_continuous(limits = c(-100, 300))+
  scale_y_continuous(limits = c(-100, 300))

```

# Diurnal Fluxes

set hour and month vectors to be able to take the averages

```{r, warning=FALSE}
df$hour = as.numeric(format(df$TIMESTAMP,'%H'))
df$month = as.numeric(format(df$TIMESTAMP,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c,hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

## NEE

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
levels(diel$month)
```

## CH4

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)

ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1*43.2),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1*43.2,
                  ymax = ch4_flux.c_fn1*43.2 + ch4_flux.c_fn2*43.2,
                  ymin = ch4_flux.c_fn1*43.2 - ch4_flux.c_fn2*43.2),
              alpha= 0.5)+
  scale_y_continuous(limits = c(-1,6))+
  facet_wrap(~month)
```

## H

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_fn1,
                  ymax = H.c_fn1 + H.c_fn2,
                  ymin = H.c_fn1 - H.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```

## LE

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_fn1,
                  ymax = LE.c_fn1 + LE.c_fn2,
                  ymin = LE.c_fn1 - LE.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
```


## Net Rad

```{r, warning=FALSE}
ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,RN_6_5_1_1_1.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = RN_6_5_1_1_1.c_fn1,
                  ymax = RN_6_5_1_1_1.c_fn1 + RN_6_5_1_1_1.c_fn2,
                  ymin = RN_6_5_1_1_1.c_fn1 - RN_6_5_1_1_1.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
levels(diel$month)
```


# Save

This gets written into data folder to match with previous cleaned files' location

Upload this file to the buckets!!!
```{r, warning=FALSE}

write.csv(x = df,file = './data/cleaned/Churchill_Met_Flux_Clean_Ameriflux_2022_2025.csv',row.names = F,quote = F)
```

