---
title: "Data Quality Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/GitHub/churchill_cleaning_processing/') #use this to set your directory
```


This file generates plots for the annual data check meetings


```{r, include = FALSE}
# Load packages, cleaned data 

rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)
library(openair)

```

<!---
# Load data
This chunk loads data, selects correct time period, and does some reformatting for plotting
-->

```{r, echo = FALSE}

df <- fread('./data/cleaned/Churchill_Met_Flux_Clean_Ameriflux_2022_2025.csv')

########### Choose Time Period #############################
#This is where you select what data you want to look at!
df <- df[df$TIMESTAMP > as.POSIXct("2025-01-01"), ]

df$TIMESTAMP <- as.POSIXct( paste(df$TIMESTAMP, "00:00"), format = "%Y-%m-%d %H:%M", tz = "UTC")

# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)
df$H.flag <- as.character(df$H.flag)
df$LE.flag <- as.character(df$LE.flag)


# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

df$H.flag <- factor(df$H.flag, levels = c("0","1","2","3","4","5"))
df$LE.flag <- factor(df$LE.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```

<!---
This chunk makes some unit adjustments and does some simple calculations - try to keep all edits here so the plots run smoothly
-->

```{r, warning=FALSE, echo = FALSE}

# Add any calculations that you want to keep throughout (make sure to adjust accordingly to site)

df$G = (df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2  # SOIL HEAT FLUX

# df<- df %>%
#   filter(!is.na(SD_10_99_1_1_1)) %>%
#   mutate(
#     SD_cm = SD_10_99_1_1_1 * 10  # adjust and convert to cm - SNOW DEPTH
#   )

df <- df %>% mutate(sonic_c = sonic_temperature - 273.15) # - SONIC TEMP

#df <- df %>% filter(!is.na(air_pressure)) %>% mutate(air_pressure_kpa = air_pressure / 1000) # -SONIC PRESSURE


df$Rn <- df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c -      # Compute net radiation 
         df$LWOUT_6_15_1_1_1.c - df$SWOUT_6_11_1_1_1.c


df$shf_avg = rowMeans(
  df[, c("SHF_6_37_1_1_1.c", "SHF_6_37_2_1_1.c")],     # Compute SHF safely with fallback
  na.rm = TRUE
)

df <- df %>%
  mutate(across(c(SWC_12_36_1_1_1, SWC_12_36_2_1_1, SWC_12_36_2_2_1), ~ .x * 100))

```


```{r, warning=FALSE, echo = FALSE}

# Subset Months and Weeks


make_week_index <- function(df, time_col = "TIMESTAMP") {

  start_month <- as.POSIXct(
    format(min(df[[time_col]]), "%Y-%m-01 00:00"),
    tz = "UTC"
  )

  df$week_in_month <- floor(
    as.numeric(difftime(df[[time_col]], start_month, units = "days")) / 7
  ) + 1

  df
}

df_month <- subset(df,
  df$TIMESTAMP >= as.POSIXct("2026-01-01 00:00", tz = "UTC")
)

df_month <- make_week_index(df_month)


```


```{r, warning=FALSE, echo = FALSE}


#BUILD A PLOTTING FUNCTION FOR CO2 AND CH4


plot_flux <- function(df, flux_base,
                      ylims, y_label,
                      title = NULL) {

  flux      <- flux_base
  flux_c    <- paste0(flux_base, ".c")
  flux_flag <- paste0(flux_base, ".flag")

  df$.__flux__      <- df[[flux]]
  df$.__flux_c__    <- df[[flux_c]]
  df$.__flux_flag__ <- df[[flux_flag]]

  ggplot(df) +
    geom_hline(yintercept = 0) +
    geom_point(
      aes(TIMESTAMP, .__flux__, color = .__flux_flag__),
      na.rm = TRUE
    ) +
    geom_point(aes(TIMESTAMP, .__flux_c__), color = "black") +
    scale_y_continuous(limits = ylims) +
    labs(
      title = title,
      x = NULL,
      y = y_label
    ) +
    scale_color_manual(
      values = color_map,
      name = "Cleaning Flag",
      na.translate = FALSE
    ) +
    theme_bw()
}

```


```{r, warning=FALSE, echo = FALSE}


# MAKE FUNCTION TO PLOT WEEKS OF CURRENT MONTH

plot_week_flux <- function(df, week_num,
                           flux_base,
                           ylims, y_label) {

  dfw <- subset(df, week_in_month == week_num)

  plot_flux(
    dfw,
    flux_base,
    ylims,
    y_label,
    title = paste("Week", week_num)
  )
}

```

# Timeseries Plots

Flag = 0, 1, 2 : EP Flag
Flag = 3 : Absolute Limits Filter
Flag = 4 : Rolling MAD Filter
Flag = 5 : Diagnostic filter


## CO2

<!-- Change these values if you adjust cleaning limits! -->

CO2 is cleaned with absolute limits of 8 & -15, and a limit of 3 MADs away from the mean over a 7 day window in the summer and 7 MADs away from the mean in the winter

#### Year-to-Date CO2 - wide range plot

```{r, warning=FALSE, echo = FALSE}

nee_plot_ytd <- plot_flux(
  df,
  "co2_flux",
  c(-30, 30),
  expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

nee_plot_ytd

```

#### Year-to-Date CO2 - limit range plot

```{r, warning=FALSE, echo = FALSE}
# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd <- plot_flux(
  df,
  "co2_flux",
  c(-12, 8),
  expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

nee_plot_ytd

```

#### Previous Month CO2

```{r, warning=FALSE, echo = FALSE}

nee_plot_month <- plot_flux(
  df_month,
  "co2_flux", 
  c(-2, 2),
  expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

nee_plot_month

```


#### Weekly CO2

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold', echo = FALSE}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month, w,
    "co2_flux", 
    c(-2, 2),
    expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  )

  plot(p)
}

```

## Methane

<!-- Change these values if you adjust cleaning limits! -->

Methane is cleaned with absolute limits of -0.15 & 0.28, and a limit of 8 MADs away from the mean over a 7 day window

#### Year to date CH4

```{r, warning=FALSE, echo = FALSE}

ch4_plot_ytd <- plot_flux(
  df,
  "ch4_flux", 
  c(-0.15, 0.4),
  expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

ch4_plot_ytd

```

#### Monthly CH4

```{r, warning=FALSE, echo = FALSE}

ch4_plot_month <- plot_flux(
  df_month,
  "ch4_flux", 
  c(-0.1, 0.1),
  expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

ch4_plot_month

```

#### Weekly CH4

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold', echo = FALSE}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month, w,
    "ch4_flux",      
    c(-0.1, 0.1),    
    expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  )

  print(p)
}

```

## Energy Fluxes, with cleaning flags

#### Year to Date H
```{r, warning=FALSE, echo=FALSE, echo = FALSE}
H_plot_ytd <- plot_flux(
  df,
  "H", 
  c(-400, 400),
  expression(paste("H (W/m²)"))
)

H_plot_ytd

```

#### H Month

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
H_plot_ytd <- plot_flux(
  df_month,
  "H", 
  c(-400, 400),
  expression(paste("H (W/m²)"))
)

H_plot_ytd

```

#### H week

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold', echo = FALSE}

for (w in sort(unique(df_month$week_in_month))) {

p <- plot_week_flux(
  df_month,w,
  "H", 
  c(-400, 400),
  expression(paste("H (W/m²)"))
)

print(p)
}

```

#### Year to Date LE

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
LE_plot_ytd <- plot_flux(
  df,
  "LE", 
  c(-100, 400),
  expression(paste("LE (W/m²)"))
)

LE_plot_ytd

```

#### LE month

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

LE_plot_month<- plot_flux(
  df_month,
  "LE", 
  c(-10, 15),
  expression(paste("LE (W/m²)"))
)

LE_plot_month

```

#### Weekly LE

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold', echo = FALSE}

for (w in sort(unique(df_month$week_in_month))) {

p <- plot_week_flux(
  df_month,w,
  "LE", 
  c(-10, 15),
  expression(paste("LE (W/m²)"))
)

print(p)
}

```

# Diurnal Fluxes

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
# set hour and month vectors to be able to take the averages

df$hour = as.numeric(format(df$TIMESTAMP,'%H'))
df$month = as.numeric(format(df$TIMESTAMP,'%m'))
df$year = as.numeric(format(df$TIMESTAMP, "%Y"))


diel = df %>%
  group_by(year,month,hour) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c,RN_6_5_1_1_1.c,`u*`,TKE,year,month,hour) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

#### NEE

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
diurnal_nee <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(year~month)
diurnal_nee
```

#### CH4

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
diurnal_ch4 <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(year~month)
diurnal_ch4

```

#### LE

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
diurnal_le <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_fn1,
                  ymax = LE.c_fn1 + LE.c_fn2,
                  ymin = LE.c_fn1 - LE.c_fn2),
              alpha= 0.5)+
  facet_wrap(year~month)
diurnal_le

```

#### H

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
diurnal_H <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_fn1,
                  ymax = H.c_fn1 + H.c_fn2,
                  ymin = H.c_fn1 - H.c_fn2),
              alpha= 0.5)+
  facet_wrap(year~month)
diurnal_H

```

#### RN

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
diurnal_RN <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,RN_6_5_1_1_1.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = RN_6_5_1_1_1.c_fn1,
                  ymax = RN_6_5_1_1_1.c_fn1 + RN_6_5_1_1_1.c_fn2,
                  ymin = RN_6_5_1_1_1.c_fn1 - RN_6_5_1_1_1.c_fn2),
              alpha= 0.5)+
  facet_wrap(year~month)
diurnal_RN

```

#### U*

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
diurnal_u. <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,`u*_fn1`),lty=2)+
  geom_ribbon(aes(x = hour,y = `u*_fn1`,
                  ymax = `u*_fn1` + `u*_fn1`,
                  ymin = `u*_fn1` - `u*_fn1`),
              alpha= 0.5)+
 facet_wrap(year~month)
diurnal_u.

```

# Energy Balance Plots

#### Full Year-to-date, color coded

```{r, warning=FALSE, echo = FALSE}

# Replace rows where both SHF were missing
both_missing <- is.na(df$SHF_6_37_1_1_1.c) & is.na(df$SHF_6_37_2_1_1.c)
df$shf_avg[both_missing] = 0  

# -------------------------------
# Compute energy balance
# -------------------------------
df$met <- df$Rn - df$shf_avg
df$flux <- df$H.c + df$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)

# Plot with month coloring
eb_ytd_month <- ggplot(df, aes(x = met, y = flux, color = factor(month))) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  scale_color_viridis_d(name = "Month") +
  labs(
    x = expression("Rn - G  (W m"^-2*")"),
    y = expression("H + LE  (W m"^-2*")"),
    title = "Churchill Full Year Energy Balance"
  ) +
  annotate(
    "text",
    x = max(x_lim), y = min(y_lim),
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()

# Print
eb_ytd_month

```

#### Previous Month EB

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

# Plot
eb_month <- ggplot(df_month, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Previous Month EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_month

```


# Met Variables

```{r, warning=FALSE, echo = FALSE}

##### Plot Builder Functions

break_gaps <- function(df, ts_col, value_col, max_gap_minutes = 60) {
    df <- as.data.frame(df) 
  df <- df[order(df[[ts_col]]), ]
  
  dt <- as.numeric(diff(df[[ts_col]]), units = "mins")
  gap <- c(FALSE, dt > max_gap_minutes)
  
  # Insert NA where gap occurs so geom_line breaks
  df[[value_col]][gap] <- NA
  
  df
}

roll_vars <- c(                         # ADD VARIABLE THAT YOU WANT TO HAVE ROOLING AVERAGE 
  "H.c",
  "LE.c",
  "G",
  "LWIN_6_14_1_1_1.c",
  "LWOUT_6_15_1_1_1.c",
  "SWIN_6_10_1_1_1.c",
  "SWOUT_6_11_1_1_1.c",
  "PPFD_7_21_1_1_1.c",
  "PPFDR_7_23_1_1_1.c"
)

roll_smooth <- function(df, ts_col, value_col, k = 96, max_na_prop = 0.25) {
    df <- as.data.frame(df) 
  df <- df[order(df[[ts_col]]), ]

  # identify time gaps
  dt <- c(0, diff(as.numeric(df[[ts_col]])) / 60)  # minutes
  gap_flag <- dt > 60

  sm <- zoo::rollapply(
    seq_len(nrow(df)),
    width = k,
    align = "center",
    fill = NA,
    FUN = function(idx) {

      x <- df[[value_col]][idx]
      gaps <- gap_flag[idx]

      # if time gap exists inside window OR too many NA → don't smooth
      if (any(gaps) || mean(is.na(x)) > max_na_prop) {
        return(NA_real_)
      } else {
        return(mean(x, na.rm = TRUE))
      }
    }
  )

  df$roll <- sm
  df
}



# ------------------------------- # Single-variable flux/energy plot # ------------------------------- 

plot_flux_single <- function(df, ts_col = "TIMESTAMP", flux_col,
                             y_label, title, color = "blue", 
                             date_breaks = "1 month", date_labels = "%b",
                             smooth = FALSE,
                             y_limits = NULL,
                             clip_smooth = NULL){

  # --- split data for line vs smooth ---
  df_line   <- break_gaps(df, ts_col, flux_col)  # for geom_line
  df_smooth <- df                                # clean data for loess

  p <- ggplot(df_line, aes(x = .data[[ts_col]])) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    geom_line(aes(x = .data[[ts_col]], y = .data[[flux_col]]),
    #geom_line(aes(y = .data[[flux_col]]),
              linewidth = 0.8, alpha = 0.6, color = color) + 
    labs(x = "", y = y_label, title = title) + 
    scale_y_continuous(
      limits = y_limits,
      expand = expansion(mult = 0.05),
      breaks = scales::pretty_breaks(n = 8)
    ) +
    scale_x_datetime(date_breaks = date_breaks, 
                     date_labels = date_labels) +
    theme_minimal() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  


  if (smooth) {

    # --- choose smoothing method based on variable ---
    if (flux_col %in% roll_vars) {

      df_roll <- roll_smooth(df_smooth, ts_col, flux_col, k = 96)

      p <- p + geom_line(
        data = df_roll,
        aes(x = .data[[ts_col]], y = .data[["roll"]]),
        #aes(x = .data[[ts_col]], y = roll),
        color = "black",
        linewidth = 0.9
      )

    } else {

      # LOESS for bounded / slow variables
      n <- nrow(df_smooth)
      span_auto <- max(min((48*2) / n, 0.2), 0.01)

      p <- p + geom_smooth(
        data = df_smooth,
       # aes(x = .data[[ts_col]], y = .data[[flux_col]]),
        aes(x = .data[[ts_col]], y = .data[[flux_col]]),
        method = "loess",
        span = span_auto,
        color = "black",
        linewidth = 0.7,
        se = FALSE
      )

      if (!is.null(clip_smooth)) {
        p <- p + coord_cartesian(ylim = clip_smooth)
      }
    }
  }

  return(p)
}

# ------------------------------- # Long-format paired-variable flux/energy plot # -------------------------------

plot_flux_long <- function(df, ts_col = "TIMESTAMP", 
                           cols, labels, colors, 
                           y_label, title, 
                           date_breaks = "1 month",
                           date_labels = "%b", 
                           smooth = FALSE) {
  
  # -------------------------------
  # RAW LINES WITH GAP BREAKS
  # -------------------------------
  raw_list <- lapply(cols, function(v) {
    
    dfv <- as.data.frame(df[, c(ts_col, v), with = FALSE])
    names(dfv) <- c(ts_col, "value")
    dfv$variable <- v
    
    dfv <- break_gaps(dfv, ts_col, "value")
    dfv
  })
  
  df_long <- do.call(rbind, raw_list)
  df_long$variable <- factor(df_long$variable, levels = cols)
  
  p <- ggplot(df_long, aes(x = .data[[ts_col]], y = value, color = variable)) +
    geom_line(alpha = 0.6, linewidth = 0.8) + 
    scale_color_manual(values = colors, labels = labels, name = NULL) + 
    scale_y_continuous(expand = expansion(mult = 0.05), 
                       breaks = scales::pretty_breaks(n = 8),
                       name = y_label) + 
    scale_x_datetime(date_breaks = date_breaks, 
                     date_labels = date_labels) + 
    labs(title = title, x = "") +
    theme_minimal() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "top") 
  
  # -------------------------------
  # SMART SMOOTHING
  # -------------------------------
  if (smooth) {
    
    smooth_list <- lapply(cols, function(v) {
      
      dfv <- as.data.frame(df[, c(ts_col, v), with = FALSE])
      names(dfv) <- c(ts_col, "value")
      dfv$variable <- v
      
      if (v %in% roll_vars) {
        dfv <- roll_smooth(dfv, ts_col, "value", k = 96)
        dfv$smooth_value <- dfv$roll
      } else {
        n <- nrow(dfv)
        span_auto <- max(min((48*2) / n, 0.2), 0.01)
        
        lo <- loess(value ~ as.numeric(dfv[[ts_col]]),
                    data = dfv,
                    span = span_auto,
                    na.action = na.exclude)
        
        dfv$smooth_value <- predict(lo)
      }
      
      dfv
    })
    
    df_smooth <- do.call(rbind, smooth_list)
    df_smooth$variable <- factor(df_smooth$variable, levels = cols)
    
    p <- p + geom_line(
      data = df_smooth,
      aes(x = .data[[ts_col]], y = smooth_value, color = variable),
      linewidth = 0.9
    )
  }
  
  return(p)
}



```

#### Year to Date H and LE

```{r, warning=FALSE, echo = FALSE}
# Sensible and latent heat fluxes stacked
p_H <- plot_flux_single(df, flux_col = "H.c",
                        y_label = "H (W/m²)",
                        title = "Sensible Heat Flux (H)",
                        color = "firebrick",
                        smooth = T)
                  
        

p_LE <- plot_flux_single(df, flux_col = "LE.c",
                         y_label = "LE (W/m²)",
                         title = "Latent Heat Flux (LE)",
                         color = "dodgerblue",
                         smooth = T)
                        
         

p_H / p_LE  # stack using patchwork

```

#### Monthly H and LE

```{r, warning=FALSE, echo = FALSE}
p_H_mo <- plot_flux_single(df_month, flux_col = "H.c",
                           y_label = "H (W/m²)",
                           title = "Sensible Heat Flux (H)",
                           color = "firebrick",
                           date_breaks = "2 days",
                           date_labels = "%b %d")

p_LE_mo <- plot_flux_single(df_month, flux_col = "LE.c",
                            y_label = "LE (W/m²)",
                            title = "Latent Heat Flux (LE)",
                            color = "dodgerblue",
                            date_breaks = "2 days",
                            date_labels = "%b %d")

p_H_mo / p_LE_mo

```

#### Year to Date Longwave Radiation

```{r, warning=FALSE, echo = FALSE}
p_lw <- plot_flux_long(df,
                       cols = c("LWIN_6_14_1_1_1.c", "LWOUT_6_15_1_1_1.c"),
                       labels = c("Incoming LW", "Outgoing LW"),
                       colors = c("firebrick", "dodgerblue"),
                       y_label = expression(Longwave~Radiation~(W/m^2)),
                       title = "Longwave Radiation In/Out",
                       date_breaks = "1 month",
                       date_labels = "%b",
                       smooth = T)
p_lw

```

#### Monthly Longwave Radiation

```{r, warning=FALSE, echo = FALSE}
p_lw <- plot_flux_long(df_month,
                       cols = c("LWIN_6_14_1_1_1.c", "LWOUT_6_15_1_1_1.c"),
                       labels = c("Incoming LW", "Outgoing LW"),
                       colors = c("firebrick", "dodgerblue"),
                       y_label = expression(Longwave~Radiation~(W/m^2)),
                       title = "Longwave Radiation In/Out",
                       date_breaks = "2 days",
                       date_labels = "%b %d")
p_lw

```

#### Year to Date Shortwave Radiation

```{r, warning=FALSE, echo = FALSE}
p_sw <- plot_flux_long(df,
                       cols = c("SWIN_6_10_1_1_1.c", "SWOUT_6_11_1_1_1.c"),
                       labels = c("Incoming SW", "Outgoing SW"),
                       colors = c("pink4", "dodgerblue4"),
                       y_label = expression(Shortwave~Radiation~(W/m^2)),
                       title = "Shortwave Radiation In/Out",
                       date_breaks = "1 month",
                       date_labels = "%b",
                       smooth = T)

p_sw

```

#### Monthly Shortwave 

```{r, warning=FALSE, echo = FALSE}
p_sw <- plot_flux_long(df_month,
                       cols = c("SWIN_6_10_1_1_1.c", "SWOUT_6_11_1_1_1.c"),
                       labels = c("Incoming SW", "Outgoing SW"),
                       colors = c("pink4", "dodgerblue4"),
                       y_label = expression(Shortwave~Radiation~(W/m^2)),
                       title = "Shortwave Radiation In/Out",
                       date_breaks = "2 days",
                       date_labels = "%b %d")

p_sw

```

#### Year to Date PAR

```{r, warning=FALSE, echo = FALSE}

p_par_IN <- plot_flux_single(df, flux_col = "PPFD_7_21_1_1_1.c",
                             y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                             title = "PAR — In",
                             color = "forestgreen",
                             date_breaks = "1 month",
                             date_labels = "%b",
                             smooth = T)

p_par_OUT <- plot_flux_single(df, flux_col = "PPFDR_7_23_1_1_1.c",
                              y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                              title = "PAR — Out",
                              color = "forestgreen",
                              date_breaks = "1 month",
                              date_labels = "%b",
                              smooth = T)

p_par_IN / p_par_OUT

```

#### Monthly PAR

```{r, warning=FALSE, echo = FALSE}

p_par_IN <- plot_flux_single(df_month, flux_col = "PPFD_7_21_1_1_1.c",
                             y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                             title = "PAR — In",
                             color = "forestgreen",
                             date_breaks = "2 days",
                             date_labels = "%b %d")

p_par_OUT <- plot_flux_single(df_month, flux_col = "PPFDR_7_23_1_1_1.c",
                              y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                              title = "PAR — Out",
                              color = "forestgreen",
                              date_breaks = "2 days",
                              date_labels = "%b %d")

p_par_IN / p_par_OUT

```

#### Year to Date Albedo

```{r, warning=FALSE, echo = FALSE}
p_albedo <- plot_flux_single(df, flux_col = "ALB_1_1_1.c",
                             y_label = "Albedo",
                             title = "Albedo",
                             color = "cyan4",
                             date_breaks = "1 month",
                             date_labels = "%b",
                             smooth = T,
                             y_limits =c(0,1),
                             clip_smooth = c(0,1)
                             )

p_albedo 
```

#### Year to Date Heat Flux (G)

```{r, warning=FALSE, echo = FALSE}
p_G <- plot_flux_single(df, flux_col = "G",
                        y_label = expression(Soil~Heat~Flux~(W/m^2)),
                        title = "Soil Heat Flux",
                        color = "blue",
                        date_breaks = "1 month",
                        date_labels = "%b",
                        smooth = F)
p_G
```

#### Monthly Heat Flux (G)

```{r, warning=FALSE, echo = FALSE}
p_G <- plot_flux_single(df_month, flux_col = "G",
                        y_label = expression(Soil~Heat~Flux~(W/m^2)),
                        title = "Soil Heat Flux",
                        color = "blue",
                        date_breaks = "2 days",
                        date_labels = "%b %d")#,
                        #smooth = FALSE)
p_G
```

#### Year to Date Soil Moisture

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

P_soilM <- plot_flux_long(
  df,
  cols = c("SWC_12_36_1_1_1",
           "SWC_12_36_2_1_1",
           "SWC_12_36_2_2_1"),
  labels = c("1.1", "2.1", "2.2"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Moisture (%)",
  title = "Soil Moisture by Depth")
P_soilM

```

#### Monthly Soil Moisture

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
P_soilM <- plot_flux_long(
  df_month,
  cols = c("SWC_12_36_1_1_1",
           "SWC_12_36_2_1_1",
           "SWC_12_36_2_2_1"),
  labels = c("1.1", "2.1", "2.2"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Moisture (%)",
  title = "Soil Moisture by Depth",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilM

```

#### Year to Date Soil Temperatures (10 - 30 cm)

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

P_soilT <- plot_flux_long(
  df,
  cols = c("TS_2_38_1_1_1.c",
           "TS_2_38_2_1_1.c",
           "TS_2_38_2_2_1.c"),
  labels = c("1.1", "2.1", "2.2"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth"
)
P_soilT

```

#### Monthly Soil Temperatures (10 -30 cm)

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
P_soilT <- plot_flux_long(
  df_month,
  cols = c("TS_2_38_1_1_1.c",
           "TS_2_38_2_1_1.c",
           "TS_2_38_2_2_1.c"),
  labels = c("1.1", "2.1", "2.2"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilT

```

#### Open Water Year to Date Soil Temperatures (0 - 100 cm)

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

P_soilT <- plot_flux_long(
  df,
  cols = c("TS_2_38_3_1_1.c",
           "TS_2_38_3_2_1.c",
           "TS_2_38_3_3_1.c",
           "TS_2_38_3_4_1.c",
           "TS_2_38_3_5_1.c",
           "TS_2_38_3_6_1.c",
           "TS_2_38_3_7_1.c",
           "TS_2_38_3_8_1.c",
           "TS_2_38_3_9_1.c",
           "TS_2_38_3_10_1.c",
           "TS_2_38_3_11_1.c",
           "TS_2_38_3_12_1.c"),
  labels = c("0", "5", "10","20", "30", "40","50", "60","70", "80", "90", "100"),
  colors = c( "brown1","lightblue","blue","pink3","violet", "lightgreen","green4","gold3", "black","brown","lightblue4","blue4"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth (cm)"
)
P_soilT

```

#### Open Water Monthly Soil Temperatures (0 - 100 cm)

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
P_soilT <- plot_flux_long(
  df_month,
cols = c("TS_2_38_3_1_1.c",
           "TS_2_38_3_2_1.c",
           "TS_2_38_3_3_1.c",
           "TS_2_38_3_4_1.c",
           "TS_2_38_3_5_1.c",
           "TS_2_38_3_6_1.c",
           "TS_2_38_3_7_1.c",
           "TS_2_38_3_8_1.c",
           "TS_2_38_3_9_1.c",
           "TS_2_38_3_10_1.c",
           "TS_2_38_3_11_1.c",
           "TS_2_38_3_12_1.c"),
  labels = c("0", "5", "10","20", "30", "40","50", "60","70", "80", "90", "100"),
  colors = c( "brown1","lightblue","blue","pink3","violet", "lightgreen","green4","gold3", "black","brown","lightblue4","blue4"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth (cm)",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilT

```

#### Hummock Year to Date Soil Temperatures (0 - 100 cm)

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

P_soilT <- plot_flux_long(
  df,
  cols = c("TS_2_38_4_1_1.c",
           "TS_2_38_4_2_1.c",
           "TS_2_38_4_3_1.c",
           "TS_2_38_4_4_1.c",
           "TS_2_38_4_5_1.c",
           "TS_2_38_4_6_1.c",
           "TS_2_38_4_7_1.c",
           "TS_2_38_4_8_1.c",
           "TS_2_38_4_9_1.c",
           "TS_2_38_4_10_1.c",
           "TS_2_38_4_11_1.c",
           "TS_2_38_4_12_1.c"),
  labels = c("0", "5", "10","20", "30", "40","50", "60","70", "80", "90", "100"),
  colors = c( "brown1","lightblue","blue","pink3","violet", "lightgreen","green4","gold3", "black","brown","lightblue4","blue4"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth (cm)"
)
P_soilT

```

#### Hummock Monthly Soil Temperatures (0 - 100 cm)

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
P_soilT <- plot_flux_long(
  df_month,
cols = c("TS_2_38_4_1_1.c",
           "TS_2_38_4_2_1.c",
           "TS_2_38_4_3_1.c",
           "TS_2_38_4_4_1.c",
           "TS_2_38_4_5_1.c",
           "TS_2_38_4_6_1.c",
           "TS_2_38_4_7_1.c",
           "TS_2_38_4_8_1.c",
           "TS_2_38_4_9_1.c",
           "TS_2_38_4_10_1.c",
           "TS_2_38_4_11_1.c",
           "TS_2_38_4_12_1.c"),
  labels = c("0", "5", "10","20", "30", "40","50", "60","70", "80", "90", "100"),
  colors = c( "brown1","lightblue","blue","pink3","violet", "lightgreen","green4","gold3", "black","brown","lightblue4","blue4"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth (cm)",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilT

```

#### Year to Date Air Temperature

```{r, warning=FALSE, echo = FALSE}
p_air <- plot_flux_single(
  df,
  flux_col = "TA_2_1_1_1_1.c",
  y_label  = "Air Temperature (°C)",
  title    = "Air Temperature",
  color    = "red",
  date_breaks = "1 month",
  date_labels = "%b"
)

p_air
```

#### Monthly Air Temperature

```{r, warning=FALSE, echo = FALSE}
p_air <- plot_flux_single(
  df_month,
  flux_col = "TA_2_1_1_1_1.c",
  y_label  = "Air Temperature (°C)",
  title    = "Air Temperature",
  color    = "red",
  date_breaks = "2 days",
  date_labels = "%b %d"
)
p_air
```

#### Sonic Pressure

```{r, warning=FALSE, echo = FALSE}
p_pres <- plot_flux_single(
  df,
  flux_col = "PA_4_2_1_1_1.c",
  y_label  = "Air Pressure (kpa)",
  title    = "Air Pressure",
  color    = "black",
  date_breaks = "1 month",
  date_labels = "%b",
  y_limits = c(90,110)
)

p_pres
 
```

#### Relative Humidity

```{r, warning=FALSE, echo = FALSE}
p_rh <- plot_flux_single(
  df,
  flux_col = "RH_19_3_1_1_1.c",
  y_label  = "Relative Humidity (%)",
  title    = "Relative Humidity ",
  color    = "lightblue4",
  date_breaks = "1 month",
  date_labels = "%b",
  smooth = T,
  y_limits = c(0,100),
  clip_smooth = c (0,100)
)

p_rh
 
```

#### Year to Date Wind

```{r,warning=FALSE, echo = FALSE}  

df_wind_openair <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  )

windRose(df_wind_openair,
         ws = "ws",
         wd = "wd",
         paddle = FALSE,
         key = TRUE,
         main = "Wind Rose")
```

#### Monthly Wind

```{r, warning=FALSE, echo = FALSE} 

df_wind_openair <- df_month %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  )

windRose(df_wind_openair,
         ws = "ws",
         wd = "wd",
         paddle = FALSE,
         key = TRUE,
         main = "Wind Rose")

```

# Sonic Temp and Air Temp Comparison

#### T air vs T sonic - full

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

full_temp_plot <- plot_flux_long(
  df,
  cols   = c("TA_2_1_1_1_1.c", "sonic_c"),
  labels = c("Air Temp", "Sonic Temp"),
  colors = c("red", "blue"),
  y_label = "Temperature (°C)",
  title   = "Air vs Sonic Temperature — Full Timeseries",
  smooth  = FALSE,           # only once!
  date_breaks = "1 month",
  date_labels = "%b"
)


full_temp_plot 
```

#### T air vs T sonic - month

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

month_temp_plot <- plot_flux_long(
  df_month,
  cols   = c("TA_2_1_1_1_1.c", "sonic_c"),
  labels = c("Air Temp", "Sonic Temp"),
  colors = c("red", "blue"),
  y_label = "Temperature (°C)",
  title   = "Air vs Sonic Temperature — Month View",
  smooth  = FALSE,
  date_breaks = "1 week",
  date_labels = "%b %d"
)

month_temp_plot
```

#### T air vs T sonic - weeks

```{r, warning=FALSE, echo=FALSE, echo = FALSE}

week_temp_plots <- lapply(
  sort(unique(df_month$week_in_month)),
  function(w) {
    plot_flux_long(
      subset(df_month, week_in_month == w),
      cols   = c("TA_2_1_1_1_1.c", "sonic_c"),
      labels = c("Air Temp", "Sonic Temp"),
      colors = c("red", "blue"),
      y_label = "Temperature (°C)",
      title   = paste("Air vs Sonic Temperature — Week", w),
      smooth  = FALSE,
      date_breaks = "1 day",
      date_labels = "%b %d"
    )
  }
)
names(week_temp_plots) <- paste0("Week_", sort(unique(df_month$week_in_month)))

week_temp_plots

```

# Potential Radiation vs. Incoming Shortwave - radiation check

```{r, warning=FALSE, echo = FALSE}

generate_rad_plots <- function(df,
                               timestamp_col,
                               value_col,
                               mode = "biweekly",
                               month_start = NULL) {
  
  # --- Time handling ---
  df[[timestamp_col]] <- as.POSIXct(df[[timestamp_col]], tz = "UTC")
  
  # Keep a FULL copy for rpot 
  df_full <- df
  
  # Filter ONLY for points/legend cleanliness
  df <- df[!is.na(df$radflag), ]
  df$radflag <- factor(df$radflag, levels = c(0, 1))
  
  # ----- Base plot (no data attached yet) -----
  base_plot <- ggplot() +
    
    # rpot from FULL continuous dataset
    geom_line(
      data = df_full,
      aes(x = .data[[timestamp_col]], y = rpot),
      color = "blue",
      linewidth = 0.6,
      na.rm = TRUE
    ) +
    
    # measured radiation from filtered dataset
    geom_point(
      data = df,
      aes(x = .data[[timestamp_col]],
          y = .data[[value_col]],
          color = radflag),
      alpha = 0.7
    ) +
    
    labs(x = "", y = value_col, color = "Rad Flag") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top") +
    scale_color_manual(
      values = c("0" = "black", "1" = "red"),
      breaks = c("0", "1"),
      drop = TRUE
    )
  
  # =========================================================
  # MODE 1 — BIWEEKLY
  # =========================================================
  if (mode == "biweekly") {
    
    start_datetime <- min(df_full[[timestamp_col]], na.rm = TRUE)
    end_datetime   <- max(df_full[[timestamp_col]], na.rm = TRUE)
    interval <- 14 * 24 * 3600
    
    current_start <- start_datetime
    plot_count <- 1
    
    while (current_start < end_datetime) {
      
      current_end <- min(current_start + interval, end_datetime)
      
      p <- base_plot +
        ggtitle(paste0(
          "Biweekly: ",
          format(current_start, "%Y-%m-%d"),
          " to ",
          format(current_end, "%Y-%m-%d")
        )) +
        scale_x_datetime(
          limits = c(current_start, current_end),
          date_breaks = "2 day",
          date_labels = "%b %d"
        )
      
      print(p)
      assign(paste0("rad_biweek_", plot_count), p, envir = .GlobalEnv)
      
      current_start <- current_end
      plot_count <- plot_count + 1
    }
  }
  
  # =========================================================
  # MODE 2 — WEEKLY INSIDE A MONTH
  # =========================================================
  if (mode == "weekly_month") {
    
    if (is.null(month_start)) {
      stop("You must provide month_start for weekly_month mode")
    }
    
    month_start <- as.POSIXct(month_start, tz = "UTC")
    month_end <- seq(month_start, length = 2, by = "1 month")[2]
    
    df_month_full <- df_full[df_full[[timestamp_col]] >= month_start &
                               df_full[[timestamp_col]] < month_end, ]
    
    df_month <- df[df[[timestamp_col]] >= month_start &
                     df[[timestamp_col]] < month_end, ]
    
    df_month <- make_week_index(df_month, timestamp_col)
    
    weeks <- sort(unique(df_month$week_in_month))
    plot_count <- 1
    
    for (w in weeks) {
      
      dfw <- df_month[df_month$week_in_month == w, ]
      start_w <- min(dfw[[timestamp_col]])
      end_w   <- max(dfw[[timestamp_col]])
      
      p <- ggplot() +
        
        # rpot still from FULL month data
        geom_line(
          data = df_month_full,
          aes(x = .data[[timestamp_col]], y = rpot),
          color = "blue",
          linewidth = 0.6,
          na.rm = TRUE
        ) +
        
        geom_point(
          data = dfw,
          aes(x = .data[[timestamp_col]],
              y = .data[[value_col]],
              color = radflag),
          alpha = 0.7
        ) +
        
        labs(x = "", y = value_col, color = "Rad Flag") +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1),
              legend.position = "top") +
        scale_color_manual(
          values = c("0" = "black", "1" = "red"),
          breaks = c("0", "1"),
          drop = TRUE
        ) +
        ggtitle(paste0(
          "Week ", w, ": ",
          format(start_w, "%b %d"),
          " to ",
          format(end_w, "%b %d, %Y")
        )) +
        scale_x_datetime(
          limits = c(start_w, end_w),
          date_breaks = "1 day",
          date_labels = "%b %d"
        )
      
      print(p)
      assign(paste0("rad_week_", plot_count), p, envir = .GlobalEnv)
      plot_count <- plot_count + 1
    }
  }
}


```

#### Year to Date, Bi - Weekly Radiation plots

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
generate_rad_plots(df,
                   "TIMESTAMP",
                   "SWIN_6_10_1_1_1",
                   mode = "biweekly")


```


#### Previous Month, Radiation Plots

```{r, warning=FALSE, echo=FALSE, echo = FALSE}
generate_rad_plots(df,
                   "TIMESTAMP",
                   "SWIN_6_10_1_1_1",
                   mode = "weekly_month",
                   month_start = "2025-11-01")

```






