---
title: "Data Quality Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/dtrangmoe/Documents/github/churchill_cleaning_processing') #use this to set your directory
```


This file generates plots for the monthly data check meetings


```{r, include=FALSE}
# Load packages, cleaned data 

rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
Sys.setenv(TZ = "UTC")
```


```{r, include = FALSE}

df <- fread('./data/cleaned/Churchill_Met_Flux_Clean_Ameriflux_2025.csv')

# create a dataframe with only the time period of interest
df_month <- subset(df, month(df$TIMESTAMP) == 10 & year(df$TIMESTAMP) == 2025)


# data formatting for flag plots

df$co2_flux.flag <- as.factor(df$co2_flux.flag)
df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```



# Timeseries Plots

Flag = 0, 1, 2 : EddyPro Quality Flag <br>
Flag = 3 : Absolute Limits Filter <br>
Flag = 4 : Rolling MAD (Mean Average Deviation) Filter <br>
Flag = 5 : Diagnostic filter <br>


## CO2

CO2 is cleaned with absolute limits of 8 & -15, and a limit of 3 MADs away from the mean over a 7 day window

#### Year-to-Date CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
  scale_x_datetime(limits = as.POSIXct(c("2025-01-01", "2025-11-30")))+
  labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
scale_color_manual(values = color_map, name = "Cleaning Flag")
nee_plot_ytd
```
<br>
Flag = 0, 1, 2 : EddyPro Quality Flag; Flag = 3 : Absolute Limits Filter; Flag = 4 : Rolling MAD (Mean Average Deviation) Filter; Flag = 5 : Diagnostic filter <br>

### Previous Month CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-10-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_month

```
<br>
Flag = 0, 1, 2 : EddyPro Quality Flag; Flag = 3 : Absolute Limits Filter; Flag = 4 : Rolling MAD (Mean Average Deviation) Filter; Flag = 5 : Diagnostic filter <br>

### Weekly Zoom-In on CO2

```{r, warning=FALSE, echo=FALSE}
interval <- 7 * 24 * 3600  # one week in seconds

# Create weekly breaks
breaks <- seq(
  from = min(df_month$TIMESTAMP),
  to   = max(df_month$TIMESTAMP),
  by   = interval
)

# Ensure last endpoint is included
breaks <- c(breaks, max(df_month$TIMESTAMP))

# Base plotting function
plot_week <- function(start, end) {
  ggplot(df) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    geom_hline(yintercept = 0) +
    geom_point(aes(TIMESTAMP, co2_flux, color = co2_flux.flag)) +
    geom_point(aes(TIMESTAMP, co2_flux.c), color = "black") +
    scale_x_datetime(limits = c(start, end), date_breaks = "1 day", date_labels = "%b %d") +
    scale_y_continuous(limits = c(-2.5, 2.5)) +
    scale_color_manual(values = color_map, name = "QC CO2 Flux") +
    labs(
      x = NULL,
      y = expression(paste(CO[2], " Flux (Âµmol m"^-2, " s"^-1, ")"))
    )
}

# Generate plots
plots <- Map(plot_week, breaks[-length(breaks)], breaks[-1])

(plots[[1]]+plots[[2]])/(plots[[3]]+plots[[4]]+plots)+
  plot_layout(guides = "collect", axes = "collect")
```


#### Week 1
```{r, warning=FALSE, echo=FALSE}
plots[[1]]
```

#### Week 2
```{r, warning=FALSE, echo=FALSE}
plots[[2]]
```

#### Week 3
```{r, warning=FALSE, echo=FALSE}
plots[[3]]
```

#### Week 4
```{r, warning=FALSE, echo=FALSE}
plots[[4]]
```
<br>
Flag = 0, 1, 2 : EddyPro Quality Flag; Flag = 3 : Absolute Limits Filter; Flag = 4 : Rolling MAD (Mean Average Deviation) Filter; Flag = 5 : Diagnostic filter<br>

## Methane

Methane is cleaned with absolute limits of -0.15 & 0.28, and a limit of 8 MADs away from the mean over a 7 day window

#### Year-to-Date Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_year = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.33))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-01-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_year

```
<br>
Flag = 0, 1, 2 : EddyPro Quality Flag; Flag = 3 : Absolute Limits Filter; Flag = 4 : Rolling MAD (Mean Average Deviation) Filter; Flag = 5 : Diagnostic filter <br>

#### Previous Month Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.2,0.2))+  
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-10-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_month

```
<br>
Flag = 0, 1, 2 : EddyPro Quality Flag; Flag = 3 : Absolute Limits Filter; Flag = 4 : Rolling MAD (Mean Average Deviation) Filter; Flag = 5 : Diagnostic filter <br>

### Weekly Zoom-In on CH4
```{r, warning=FALSE, echo=FALSE}
interval <- 7 * 24 * 3600  # one week in seconds

# Create weekly breaks
breaks <- seq(
  from = min(df_month$TIMESTAMP),
  to   = max(df_month$TIMESTAMP),
  by   = interval
)

# Ensure last endpoint is included
breaks <- c(breaks, max(df_month$TIMESTAMP))

# Base plotting function
plot_week <- function(start, end) {
  ggplot(df) +
    geom_hline(yintercept = 0) +
    geom_point(aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag)) +
    geom_point(aes(TIMESTAMP, ch4_flux.c), color = "black") +
    scale_x_datetime(limits = c(start, end)) +
    scale_y_continuous(limits = c(-0.2, 0.2)) +
    scale_color_manual(values = color_map, name = "QC CH4 Flux") +
    labs(
      x = NULL,
      y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
    )
}

# Generate plots
plots <- Map(plot_week, breaks[-length(breaks)], breaks[-1])

# Arrange
(plots[[1]] / plots[[2]] /
plots[[3]] / plots[[4]]) +
  plot_layout(guides = "collect", axes = "collect")
```
<br>
Flag = 0, 1, 2 : EddyPro Quality Flag; Flag = 3 : Absolute Limits Filter; Flag = 4 : Rolling MAD (Mean Average Deviation) Filter; Flag = 5 : Diagnostic filter <br>

# Energy Balance Plots

#### Full Year-to-date
```{r, warning=FALSE, echo=FALSE}

df$met = ((df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c) -
         (df$LWOUT_6_15_1_1_1.c + df$SWOUT_6_11_1_1_1.c)) -
        ((df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2)
df$flux = df$H.c + df$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df)
summary_mod = summary(mod)

# Extract slope and RÂ˛
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nRÂ˛:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)


# Plot
eb_ytd <- ggplot(df, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Full Year EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nRÂ˛ = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_ytd
```


#### Previous Month
```{r, warning=FALSE, echo=FALSE}

df_month$met = ((df_month$LWIN_6_14_1_1_1.c + df_month$SWIN_6_10_1_1_1.c) -
         (df_month$LWOUT_6_15_1_1_1.c + df_month$SWOUT_6_11_1_1_1.c)) -
        ((df_month$SHF_6_37_1_1_1.c + df_month$SHF_6_37_2_1_1.c)/2)
df_month$flux = df_month$H.c + df_month$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df_month)
summary_mod = summary(mod)

# Extract slope and RÂ˛
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nRÂ˛:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)

# Plot
eb_month <- ggplot(df_month, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Previous Month EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nRÂ˛ = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_month

```



# Timestamp Alignment Check

Measured shortwave radiation vs. calculated potential radiation <br>
Most points should be below the 1:1 line in these plots (where measured radiation is below potential radiation)

#### Full Year-to-Date
```{r, warning=FALSE, echo=FALSE}
ggplot(data = df)+
  geom_point(aes(x = rpot, y = SWIN_6_10_1_1_1, color = radflag))+
  geom_abline(yint = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(0, 1000))+
  scale_y_continuous(limits = c(0, 1000))+
  labs(
    x = expression("Measured Radiation (SW In)"),
    y = expression("Calculated Potential Radiation"),
    title = NULL
  )

```


#### Previous Month
```{r, warning=FALSE, echo=FALSE}

ggplot(data = df_month)+
  geom_point(aes(x = rpot, y = SWIN_6_10_1_1_1, color = radflag))+
  geom_abline(yint = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(0, 1000))+
  scale_y_continuous(limits = c(0, 1000))+
  labs(
    x = expression("Measured Radiation (SW In)"),
    y = expression("Calculated Potential Radiation"),
    title = NULL
  )

```


# Diurnal Fluxes

```{r, warning=FALSE, echo=FALSE}
# set hour and month vectors to be able to take the averages

df <- dplyr::filter(df, !df$TIMESTAMP < as.POSIXct("2022-09-01 00:00:00"))

df$hour = as.numeric(format(df$TIMESTAMP,'%H'))
df$month = as.numeric(format(df$TIMESTAMP,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c,hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)
  

diel = subset(diel,!is.na(diel$month))
```

#### NEE Diurnals

```{r, warning=FALSE, echo=FALSE}
diurnal_nee <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)+
  labs(
    x = expression("Hour"),
    y = expression(paste(CO[2], " Flux (Âµmol m"^-2, " s"^-1, ")")),
    title = NULL
  )
diurnal_nee
```

#### CH4 Diurnals

```{r, warning=FALSE, echo=FALSE}
diurnal_ch4 <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)+
  labs(
    x = expression("Hour"),
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")")),
    title = NULL
  )
diurnal_ch4

```

